### 2019-09-05 MSimonsHW1.tex
1a and 1b for HW1

\documentclass{article}
\title{Homework 1}
\author{Madilyn Simons}
\date{}
\setlength{\parindent}{0pt}
\pdfpagewidth 8.5in
\pdfpageheight 11in

\begin{document}
\maketitle

\begin{enumerate}

\item \textbf{a} We can prove the statement by induction.  First, let $n = 1$.  As such, $n^2 = 1$.  By the Division Algorithm, $n^2 = 8*0 + 1$.  Thus, the statement holds for $n = 1$.  Next, assume the statement holds for $1, 3, 5, ..., n$.  Since $n$ is odd, the next consecutive odd number is $n+2$.  Because $n^2$ leaves a remainder of 1 when divided by 8, let $n^2 = 8*k + 1$ for some integer $k$.  As such, $(n+2)^2 = n^2 + 4*n + 4 = 64*k^2 + 48*k + 9 = 8 * (8*k^2 + 6*k + 1) + 1$.  Hence, $(n+2)^2$ leaves a remainder of 1 when divided by 8.  By induction, for any odd number $n$, $n$ leaves a remainder of 1 when divided by 8.

\textbf{b} Let $n = 2^{a_0} * {p_1}^{a_1} * {p_2}^{a_2} * ... * {p_k}^{a_k}$ be the prime factorization of $n$ such that $p_i$ are distinct prime numbers for all $i$ and there is no $i$ such that $p_i = 2$.  As such, $n^2 = 2^{2a_0} * {p_1}^{2a_1} * {p_2}^{2a_2} * ... * {p_k}^{2a_k}$.  Since $p_i$ is odd for all $i$ (since all $p_i$ are primes and do not equal 2), ${p_1}^{a_1} * {p_2}^{a_2} * ... * {p_k}^{a_k}$ is also odd.  By $1a$, ${p_1}^{2a_1} * {p_2}^{2a_2} * ... * {p_k}^{2a_k}$ leaves a remainder of 1 when divided by 8.  Let ${p_1}^{2a_1} * {p_2}^{2a_2} * ... * {p_k}^{2a_k} = 8b + 1$ for some integer $b$.  Thus, $n^2 = 2^{2a_0} * (8b + 1) = 4^{a_0} * (8b + 1) = (8 * (4^{a_0}b) + 4^{a_0}).$  Since factors of 4 can only leave a remainder of either 0 or 4 when divided by 8 $n^2 = (8 * (4^{a_0}b) + 4^{a_0})$, $n^2$ can only leave a remainder or 0 or 4 when divided by 8.

\item \textbf{Problem:} Three calculus books weigh as much as two geometry books.  Seven geometry books weigh as much as nine algebra books.  Six trigonometry books weigh as much as eleven calculus books.  How many algebra books weigh as much as $21$ trigonometry books? \\

\textbf{Solution:} Letting $C$ represent the weight of each calculus book, $G$ represent the weight of each geometry book, $A$ represent the weight of each algebra book, and $T$ represent the weight of each trigonometry book, we can turn the given statements into math equations: \\
\begin{eqnarray*}
3C &=& 2G \\
7G &=& 9A \\
6T &=& 11C
\end{eqnarray*}
Solving each equation for one variable or the other, we get: \\
\begin{eqnarray*}
C &=& \frac{2}{3} \cdot G \\
G &=& \frac{9}{7} \cdot A \\
C &=& \frac{6}{11} \cdot T
\end{eqnarray*}
Then, subsituting $\frac{9}{7} A$ for $G$ into the first equation, we get $C = \frac{2}{3} \cdot \frac{9}{7} A = \frac{6}{7} A$.  But we also found that $C = \frac{6}{11} T$.  Therefore $\frac{6}{7} A =  \frac{6}{11} T$, from which it follows that $11A = 7T$.  Multiplying both sides by 3 yields $33A = 21T$, so \textbf{33} algebra books have the same weight as 21 trigonometry books.

\item \textbf{Problem:} Notice that the product of the digits of $124$ is $8$.  For many other three-digit positive integers is the product of the digits equal to $8$? \\

\textbf{Solution:} We look for triples of numbers that multiply to 8.  The triples are: \\
$(1,1,8)$ since $1 \cdot 1 \cdot 8 = 8$ \\
$(1,2,4)$ since $1 \cdot 2 \cdot 4 = 8$ \\
$(2,2,2)$ since $2 \cdot 2 \cdot 2 = 8$ \\

There are $3$ ways to arrange $(1,1,8)$: $118, 181, 811$. \\
There are $6$ ways to arrange $(1,2,4)$: $124, 142, 214, 241, 412, 421$ \\
There is only one way to arrange $(2,2,2)$: $222$ \\

In all, there are $6+3+1 = 10$ ways of arranging one of the three triples that multiply to $8$.  Therefore there are $10$ numbers with a product of digits equal to $8$.  But we were asked for numbers \textit{other} than $124$; therefore, there are only $\mathbf{9}$ numbers with the desired property.

\item \textbf{Problem:} Steven takes his favorite number and adds $7$, multiplies the resulting number by $6$, squares the resulting number, and divides by $9$.  The final result of these operations is $16$.  Given that Steven's favorite number is not $5$, what is his favorite number? \\

\textbf{Solution:} Let $x$ represent Steven's favorite number.  Then \\
$\displaystyle \frac{[6(x+7)]^2}{9} = 16$. \\
$[6(x+7)]^2 = 144$ \\
$6(x+7) = \pm 12$ \\
$x+7 = 2$ or $x + 7 = -2$ \\
$x = 9$ or $x = 5$. But we were told that $x$ is not $5$.  Thus, $x = \mathbf{9}$.

\item \textbf{Problem:} Given that $a$, $b$, and $c$ are all positive, and that $ab = 21$, $ac = 18$, and $bc = 42$, find $a + b + c$. \\

\textbf{Solution:} Since $ab = 21$ and $ac = 18$, $\displaystyle \frac{c}{b} = \frac{(ac)}{(ab)} = \frac{18}{21} = \frac{6}{7}$. Multiplying the equations $\displaystyle \frac{c}{b} = \frac{6}{7}$ and $bc = 42$, we obtain $c^2 = 36$, so $c = \pm 6$.  But $c$ is positive, so $c = 6$.  Substituting this into $ac = 18$, we get $6a = 18$, so $a = 3$.  Substituting $c = 6$ into $bc = 42$, we get $6b = 42$, so $b = 7$.  Thus $a + b + c = 3 + 7 + 6 = \mathbf{16}$.

\item \textbf{Problem:} If $\displaystyle \frac{x}{4y} = \frac{y}{4z}$, find the value of $3y^4 - 3(xz)^2 + 3$.  \\

\textbf{Solution:} Multiplying both sides of $\displaystyle \frac{x}{4y} = \frac{y}{4z}$ by $4yz$ yields
$xz = y^2$. \\

Substituting $y^2$ in for $xz$, $3y^4 - 3(xz)^2 + 3$ becomes \\
$3y^4 - 3(y^2)^2 + 3 = 3y^4 - 3y^4 + 3 = \mathbf{3}$.

\item \textbf{Problem:} Given the sequence $2, 4, 6, 10, 16, 26, \ldots,$ find the $12$th term. \\

\textbf{Solution:} Notice that each term after the $3$rd term is equal to the sum of the previous two terms.  Thus, the $7$th term is $16 + 26 = 42$, the $8$th term is $26 + 42 = 68$, the $9$th term is $42 + 68 = 110$, the $10$th term is $68 + 110 = 178$, the $11$th term is $110 + 178 = 288$, and the $12$th term is $178 + 288 = \mathbf{466}$.

\item \textbf{Problem:} Bill will be $x$ years old in the year $x^2$.  If Bill was born between $1900$ and $2000$, in what year was he born? \\

\textbf{Solution:} Since Bill will be $x$ years old in the year $x^2$, he was 0 (that is, he was born) in the year $x^2 - x$.  We are given that $1900 < x^2 - x < 2000$.  Trying a few values of $x$, we find that when $x = 44$, $x^2 - x = 1892$, when $x = 45, x^2 - x = 1980$, when $x = 46, x^2 - x = 2070$, and so on.  Since only when $x = 45$ is Bill's birth year between $1900$ and $2000$, we conclude that $x = 45$, so his birth year was $\mathbf{1980}$.

\item \textbf{Problem:} Five fair coins are tossed.  What is the probability that exactly two heads and three tails turn up?  Express your answer as a decimal. \\

\textbf{Solution:} If five heads are tossed, there are $2^5 = 32$ outcomes.  The number of outcomes with $0, 1, 2, 3, 4,$ and $5$ heads correspond to the 5th row of pascal's triangle: $1, 5, 10, 10, 5, 1$, respectively.  That is, there is $1$ way to get $0$ heads, there are $5$ ways to get $1$ head, there are $10$ ways to get $2$ heads, and so on.  Since there are $10$ ways to get $2$ heads, the probability of getting exactly $2$ heads is $\frac{10}{32} = \mathbf{\frac{5}{16}}$.

\item \textbf{Problem:} Define a ``strange number'' to be a number where each digit (other than the
leftmost two) is equal to the sum of the two digits to the left.  For
instance, $11235$ is a strange number because $2 = 1 + 1$, $3 = 1 + 2$, and $5 =  2
+ 3$.  How many four-digit strange numbers are there? \\

\textbf{Solution:} Suppose the first two digits are $(a)$ and $(b)$.  Then the third digit is
$(a+b)$ and the fourth digit is $(a+2b)$.  Clearly, the values of $a$ and $b$ determine
the rest of the number.  So we only need to choose values for the first two
numbers, then evaluate the rest.  For instance, if $a = 1$ and $b = 0$, then
$(a+b) = 1$ and $a+2b) = 1$; hence, $1011$ is a ``strange number''.  If $a = 1$ and $b
= 1$, then $(a+b) = 2$ and $(a+2b) = 3$; hence, $1123$ is a ``strange number''.
Using the same process, we conclude that the following are all ``strange
numbers'': 1011, 1123, 1235, 1347, 1459, 2022, 2135, 2246, 2358, 3033, 3145, 3257, 3369, 4044, 4156, 4268, 5055, 5167, 5279, 6066, 6178, 7077, 7189, 8088, 9099.  In all, there are $\mathbf{25}$ $4$-digit ``strange numbers''.

\item \textbf{Problem:} Blues, Inc. sells jeans at the following prices: $\$15$ per pair if you buy
$1-10$ pairs, $\$13$ per pair if you buy $11-40$ pairs, $\$10$ if you buy $41-70$ pairs,
and $\$8$ per pair if you buy $71$ or more pairs.  For how many values of $n$ is it
cheaper to buy a number of pairs greater than $n$ than it is to buy exactly $n$
pairs? \\

\textbf{Solution:} \\
1 pair costs $\$15$ \\
2 pairs costs $\$30$ \\
\ldots \\
9 pairs costs $\$135$ \\
10 pairs costs $\$150$ \\

But for 11 pairs, it only costs $\$13$ per pair, so \\
11 pairs costs $\$143$ \\
12 pairs costs $\$156$ \\
\ldots  \\
31 pairs costs $\$403$ \\
32 pairs costs $\$416$ \\
\ldots  \\
40 pairs costs $\$520$ \\

But for 41 pairs, it only costs $\$10$ per pair, so \\
41 pairs costs $\$410$ \\
\ldots  \\
56 pairs costs $\$560$ \\
57 pairs costs $\$570$ \\
\ldots  \\
70 pairs costs $\$700$ \\

For 71 pairs, it costs only $\$8$ per pair, so \\
71 pairs costs $\$568$ \\
\ldots \\
100 pairs costs $\$800$ \\

Clearly, it costs more to buy $10$ pairs than it does for $11$, so we have found
$1$ value for $n$.  Similarly, it costs more to buy $32, 33, \ldots, 40$ pairs than
it does to buy $41$, so we have found 9 more values for $n$.  Finally, it costs
more to buy $57, 58, \ldots, 70$ pairs than it does to buy 71, so we have found
$14$ more values for $n$.  In all, there are $1 + 9 + 14 = \mathbf{24}$ values of $n$.

\item \textbf{Problem:} For what value(s) of $k$ will the equation $x^3 - 9x^2 + kx$ have exactly two solutions? \\

\textbf{Solution:} Factoring the $x$ out of $x^3 - 9x^2 + kx=0$, we obtain $x(x^2 - 9x + k)=0$ \\

One solution is $x=0$.  So $x^2 - 9x + k = 0$ must contribute one more solution.  This will only happen if $x^2 - 9x + k$ is a perfect square, or if one of the roots of $x^2 - 9x + k = 0$ is also $0$.  In the latter case, one root will be $0$ only if another $x$ can be factored out, which can only take place if $k=0$.  So one value of $k$ is $0$.  The the former case, since a perfect square is of the form $a^2 + 2ab + b^2$, we have \\

$a^2 = x^2$ \\
$2ab = -9x$ \\
$b^2 = k$ \\

Since $a^2 = x^2, x = a$.  \\
Substituting $a = x$ into $2ab = -9x$, we find that $b = -\frac{9}{2}$.  $k = b^2 = \frac{81}{4}$.  In all, $k = \mathbf{0}$ or $\displaystyle \mathbf{\frac{81}{4}}$

\item \textbf{Problem:} In a group of $200$ students, $170$ are taking history, $190$ are taking math, $160$ are taking english, and $135$ are taking art.  What is the minimum number of students that must be taking all four of these classes? \\

\textbf{Solution:} In the ``worst-case scenario'', as many students as possible are taking three, but not four, classes.  Since $170$ are taking history, $30$ aren't; since $190$ are taking math, $10$ aren't; since $160$ are taking english, $40$ aren't; and since 135 are taking art, 65 aren't.  Thus, at most $30 + 10 + 40 + 65 = 145$ aren't taking exactly one class; in this case, the other $200 - 145 = \mathbf{55}$ must be taking all four classes.

\item \textbf{Problem:} Find the smallest value of $x$ that satisfies $\sqrt{x^2 - 3x} + \sqrt{x^2 - 1} = 2$. \\

\textbf{Solution:}
Subtracting $\sqrt{x^2 - 1}$ from both sides, we get \\
\begin{eqnarray*}
\sqrt{x^2 - 3x} &=& 2 - \sqrt{x^2 - 1} \\
x^2 - 3x &=& 4 - 4\sqrt{x^2 - 1} + (\sqrt{x^2 - 1})^2 \\
x^2 - 3x &=& 4 - 4\sqrt{x^2 - 1} + x^2 - 1 \\
4\sqrt{x^2 - 1} &=& 3 + 3x \\
16(x^2 - 1) &=& 9 + 18x + 9x^2 \\
16x^2 - 16 &=& 9 + 18x + 9x^2 \\
7x^2 - 18x - 25 &=& 0 \\
7x^2 + 7x - 25x - 25 &=& 0 \\
7x(x+1) - 25(x+1) &=& 0 \\
(7x-25)(x+1) &=& 0 \\
x = 25/7 \quad \textrm{or} \quad -1.
\end{eqnarray*}
The smallest value is $x = \mathbf{-1}$.

\item \textbf{Problem:} At a cookie shop, four different kinds of cookies are sold: chocolate chip, macaroon, peanut butter, and white chocolate.  In how many different ways can a person choose eight cookies?  (Assume that the shop has an ample supply of each variety of cookie.)

\textbf{Solution:} Imagine we have 8 sticks, and we're going to put them in different piles according to how many cookies of each type Pedro buys.  The first pile corresponds to the number of chocolate cookies, the second corresponds to the number of macaroons, etc.  So 3 cookies in the first pile, 0 in the second, 2 in the third, and 3 in the fourth corresponds to 3 chocolate, 0 macaroon, 2 peanut butter, and 3 white chocolate.  We can express any set of cookies that Pedro buys in this fashion.

Now, suppose we separate the piles with dividers.  We'll need 3 dividers, since we need to separate chocolate from macaroon, macaroon from peanut butter, and peanut butter from white chocolate.  Thus, the 3, 0, 2, 3 cookie example that we had before could be expressed as:

$* * * | | * * | * * *$

Where each $*$ represents a cookie and each $|$ represents a divider.

We have 11 objects (8 cookies and 3 dividers), and they can be arranged in any order; each order corresponds to a different set of cookies.  For example the order

$ | | | * * * * * * * *$

means that we have 8 white chocolate cookies, while the order

$ | * * | * * * * * * |$

means that we have 0 chocolate, 2 macaroons, 6 peanut butter, and 0 white chocolate cookies.

So all we need to do is find the number of ways to arrange the 11 objects, or alternatively, the number of ways to pick which 3 of the 11 objects will be the dividers.  This is $\displaystyle {11\choose 3} = \frac{11!}{8!3!} = \mathbf{165}$.

\item \textbf{Problem:} The number $\sqrt{8 - 2 \sqrt{15}}$ can be expressed in the form $\sqrt{x} - \sqrt{y}$, where $x$ and $y$ are positive integers.  Find $2x+y$. \\

\textbf{Solution:}
\begin{eqnarray*}
\sqrt{8 - 2 \sqrt{15}} &=& \sqrt{5 - 2\sqrt{15} + 3} \\
&=& \sqrt{(\sqrt{5})^2 - 2\sqrt{5} \sqrt{3} + (\sqrt{3})^2}  \\
&=& \sqrt{(\sqrt{5} - \sqrt{3})^2} \\
&=& \sqrt{5} - \sqrt{3}.
\end{eqnarray*}

So $x = 5$ and $y = 3$; $2x + y = \mathbf{13}$.

\item \textbf{Problem:} Bob is throwing turtles at a dartboard with two regions.  If he hits the smaller region, he gets $15$ points; if he hits the larger region, he gets $7$ points.  What is the largest score that Bob cannot get? \\

\textbf{Solution 1:} Bob can get the following scores: 7, 14, 15, 21, 22, 28, 29, 30, 35, 36, 37, 42, 43, 44, 45, 49, 50, 51, 52, 56, 57, 58, 59, 60, 63, 64, 65, 66, 67, 70, 71, 72, 73, 74, 75, 77, 78, 79, 80, 81, 82, 84, 85, 86, 87, 88, 89, 90, 91, \ldots  \\

After 84, all numbers are possible, so the last non-possible score is $\mathbf{83}$. \\

\textbf{Solution 2:} The numbers $7, 14, 21, 28, \ldots$ are all achievable by getting a number of $7$s.  We can get certain other numbers by substituting a $15$ for two $7$s, which will net one more point (for exmaple, when we have $4$ $7$s = $28$, we can substitute two of those $7$s for a $15$ to get $29$, or we can substitute four of the $7$s for $2$ $15$s to get $30$.)  Thus, after the number $14$, we can net $1$ point, after $28$, we can net $2$, after $42$, we can net $3$, and so on.  After $70$, we can net $5$, which means that we can get any number of points between $1$ and $5$ more than a multiple of $7$.  This includes all numbers except $76$ and $83$, which are $6$ more than a multiple of $7$. \\

Then, after $84$, we can net $6$, which means that we can get any number of points between $1$ and $6$ more than a multiple of $7$.  But this includes all numbers, since any number is either a multiple of $7$ or $1, 2, 3, 4, 5$, or $6$ more than a multiple of $7$.  Thus after $84$, we can get all numbers.  Thus the last non-possible score must be $\mathbf{83}$. \\

\textbf{Solution 3:} The answer may be obtained by using the following formula:
\[G = ab - a - b\]
where $G$ is the greatest non-possible sum that can be achieved by adding multiples of $a$ and $b$, and $a$ and $b$ are relatively prime integers.  In this case, since $a = 15$ and $b = 7$, the greatest non-possible score is $15 \cdot 7 - 15 - 7 = \mathbf{83}$.

\item \textbf{Problem:} A tennis tournament starts out with $140$ players.  Each game is played between two players; at the end of the game, the winner advances and the loser is knocked out.  There are no ties.  If the tournament has a minimum number of byes, how many games must be played to determine a single winner? \\

\textbf{Solution:} Here is a case where the solution is shorter than the problem!  Since we started with $140$ players, exactly $139$ players must be eliminated to declare one winner. But each game eliminates one player. Thus, $\mathbf{139}$ games must be played.

\item \textbf{Problem:} How many positive integers less than or equal to $1000$ are multiples of $2$ or $3$? \\

\textbf{Solution:} First of all, how many positive integers less than or equal to 1000 are multiples of 2?  The numbers are $2, 4, \ldots 1000$, that is, $500$ numbers.   Now, how many positive integers less than or equal to $1000$ are multiples of $3$?  The numbers $3, 6, \ldots 999$ are, that is, $333$ numbers.  So at first glance, it seems like there are $500 + 333 = 833$ numbers.  However, we've counted some numbers twice.  For instance, $6$ was counted in both the multiples-of-two and the multiples-of-three list.  In fact, all multiples of both $2$ and $3$ - that is, multiples of $2 \cdot 3 = 6$ - have been counted twice.  These numbers are $6, 12, 18, \ldots 996$, that is, $166$ numbers.  Since we've counted $166$ numbers twice, we need to subtract them off once to leave only one copy of them.  $833 - 166 = \mathbf{667}$ numbers.

\item \textbf{Problem:} Find $x^2 + y^2 + z^2$ if
\begin{eqnarray}
x + y + z = 3 \\
2x - y + z = 5 \\
3x + 2y - z = 16
\end{eqnarray}

\textbf{Solution:}

Adding $(1)$ and $(2)$ together yields $3x + 2z = 8$ \\

Adding $2 \cdot (2)$ and $(3)$ together yields $7x + z = 26$.  Multiplying this by $2$ yields $14x + 2z = 52$. \\

So now we have
\begin{eqnarray}
14x + 2z = 52 \\
3x + 2z = 8
\end{eqnarray}

Subtracting (5) from (4) yields $11x = 44$, so $x = 4$.  Plugging this into $3x + 2z = 8$, we have $3 \cdot 4 + 2z = 8$, so $2z = -4$, so $z = -2$.  Finally, plugging these values of $x$ and $z$ into $x + y + z = 3$ yields $4 + y + -2 = 3$, so $y = 1$.  Thus, $x^2 + y^2 + z^2 = 4^2 + 1^2 + (-2)^2 = 16 + 1 + 4 = \mathbf{21}$.

\item \textbf{Problem:} Find the length of the longest median of a triangle with sides of length $4$, $7$, and $9$.  \\

\textbf{Solution:} Let the triangle have vertices $A, B,$ and $C$, with $AB = 4$, $AC = 7$, and $BC = 9$.  The longest median will be the median to the shortest side.  Thus, we wish to find the length of the line from C to the midpoint of AB, which we will call $M$.  (Since $M$ is the midpoint of $AB$, $AM = MB = 2$.) \\

Now extend $CM$ past point $M$ to another point D so that $DM = CM$.   Since $AM = BM$ and $CM = DM$, the diagonals of quadrilateral ACBD bisect each other.  This means that ACBD is a parallelogram.  Since opposite sides of a parallelogram are equal, $BD = CA = 7$ and $AD = CB = 9$. \\

Finally, we use the following property of a parallelogram: the sum of the squares of the diagonals are equal to the sum of the squares of the four sides.  In math terms, this means that $AB^2 + CD ^2 = AD^2 + DB^2 + BC^2 + CA^2$.  Plugging in the values that we know ($AB = 4, AD = 9, DB = 7, BC = 9, CA = 7$), we get the following equation: \\
\begin{eqnarray*}
4^2 + CD^2 &=& 9^2 + 7^2 + 9^2 + 7^2 \\
16 + CD^2 &=& 260 \\
CD^2 &=& 244 \\
CD &=& \sqrt{244} = 2\sqrt{61}
\end{eqnarray*}
Since $M$ is the midpoint of $CD$, $CM = \frac{CD}{2} = 1/2 \cdot 2 \sqrt{61} = \mathbf{\sqrt{61}}$.

\item \textbf{Problem:} If $\displaystyle x + \frac{1}{x} = 8$, find the value of $\displaystyle x^4 + \frac{1}{x^4}$.

\textbf{Solution:} Squaring both sides of the equation $x + \frac{1}{x} = 8$ yields \\
\begin{eqnarray*}
x^2 + 2\cdot x \cdot \frac{1}{x} + \left(\frac{1}{x} \right)^2 &=& 64 \\
x^2 + 2 + \frac{1}{x^2} &=& 64 \\
x^2 + \frac{1}{x^2} &=& 62
\end{eqnarray*}

Squaring both sides of this equation yields
\begin{eqnarray*}
(x^2)^2 + 2 \cdot x^2 \cdot \frac{1}{x^2} + \left(\frac{1}{x^2} \right)^2 &=& 3844 \\
x^4 + 2 + 1/x^4 &=& 3844 \\
x^4 + 1/x^4 &=& \mathbf{3842}
\end{eqnarray*}

\item \textbf{Problem:} If the prime factorization of positive integer $N$ is ${2}^{4} \cdot {3}^{9} \cdot {11}^{121}$, then how many positive integer factors does $N$ have?

\textbf{Solution:} If a number has a prime factorization of $a^A \cdot b^B \cdot c^C \cdot d^D \cdots$, then it has $(A+1)(B+1)(C+1) \ldots$ factors.

Since N has the factorization $2^4 \cdot 3^9 \cdot 11^{121}$, it has $(4+1)(9+1)(121+1) = 5 \cdot 10 \cdot 122 = \mathbf{6100}$ factors.

\item \textbf{Problem:} If $2^{16x^2 - 4x + 7} = 16^{x^2 + 2x + 1}$, what is $x$?  \\

\textbf{Solution:}
\begin{eqnarray*}
2^{16x^2 - 4x + 7} &=& (2^4)^{x^2 + 2x + 1} \\
2^{16x^2 - 4x + 7} &=& 2^{4(x^2 + 2x + 1)} \\
2^{16x^2 - 4x + 7} &=& 2^{4x^2 + 8x + 4} \\
16x^2 - 4x + 7 &=& 4x^2 + 8x + 4 \\
12x^2 - 12x + 3 &=& 0 \\
x^2 - x + \frac{1}{4} &=& 0 \\
(x-\frac{1}{2})(x-\frac{1}{2}) &=& 0 \\
(x-\frac{1}{2})^2 &=& 0 \\
(x - \frac{1}{2}) &=& 0 \\
x &=& \mathbf{\frac{1}{2}}
\end{eqnarray*}.

\item \textbf{Problem:} For certain integers $n$, $n^2 - 3n - 126$ is a perfect square.   What is the sum of all distinct possible values of $n$? \\

\textbf{Solution:} Since $n^2 - 3n - 126$ is a perfect square, we can say that $n^2 - 3n - 126 = k^2$ for some integer k.  Multiplying this equation by four, we get
\[4n^2 - 12n - 504 = 4k^2\]

Replacing $-504$ with $9-513$, since the two are equal, we get
\begin{eqnarray*}
(2n)^2 - 12n + (9-513) &=& 4k^2 \\
(2n)^2 - 2(2n)(3) + 3^2 - 513 &=& 4k^2
\end{eqnarray*}

The first three terms on the left side are of the form $a^2 - 2ab + b^2$, where $a = 2n$ and $b = 3$.  Remembering that $a^2 - 2ab + b^2 = (a-b)^2$, we get
\begin{eqnarray*}
(2n - 3)^2 - 513 &=& 4k^2 \\
(2n - 3)^2 - 4k^2 - 513 &=& 0 \\
(2n - 3)^2 - (2k)^2 &=& 513
\end{eqnarray*}

Now, the left hand side is of the form $a^2 - b^2$, which factors to $(a+b)(a-b)$.  Hence, we can rewrite the equation as
\[(2n - 3 + 2k)(2n - 3 - 2k) = 513\] \\
$n$ and $k$ are both integers, so $2n - 3 + 2k$ and $2n - 3 - 2k$ are both integers as well.  So we just need to find pairs of integers whose product is $513$. \\

$513 = 3^3 \cdot 19$, so $513$'s factors are {$1,3,9,19,27,57,171,513$}.  Pairs of integers whose product is 513 are $(1,513), (3,171), (9,57), (19,27), (-1,-513),$ $(-3,-171), (-9,-57), (-19,-27),$ and all ordered pairs with the two values switched around (for instance, $(513,1)$). \\

Say we have a pair of positive integers $(x,y)$ whose product is $513$.  Then
\[2n - 3 + 2k = x\] and \[2n - 3 - 2k = y\]

Adding these two equations together, we get
\begin{eqnarray*}
4n - 6 &=& x + y \\
4n &=& x + y + 6
\displaystyle n = \frac{x+y+6}{4} \\
\end{eqnarray*}

Now, we just substitute $x$ and $y$ for each ordered pair that we found above. \\

For (1,513), $n = (1+513+6)/4 = 130$ \\
For (3,171), $n = (3+171+6)/4 = 45$ \\
For (9,57), $n = (9+57+6)/4 = 18$ \\
For (19,27), $n = (19+27+6)/4 = 13$ \\
For (-1,-513), $n = (-1-513+6)/4 = -127$ \\
For (-3, -171), $n = (-3-171+6)/4 = -42$ \\
For (-9, -57), $n = (-9-57 +6)/4 = -15$ \\
For (-19, -27), $n = (-19-27+6)/4 = -10$ \\

$130 + 45 + 18 + 13 - 127 - 42 - 15 - 10 = 12$.  This is our answer.

\item \textbf{Problem:} The function $f(x)$ is a cubic polynomial of the form $ax^3 + bx^2 + cx + d$.  Given that $f(0) = 7, f(1) = 10, f(2) = 15,$ and $f(3) = 28$, find $a + 2b + 3c + 4d$. \\

\textbf{Solution:} Since $f(0) = 7$,
\begin{eqnarray*}
7 &=& a(0)^3 + b(0)^2 + c(0) + d \\
7 &=& d
\end{eqnarray*}
Since $f(1) = 10$,
\begin{eqnarray*}
10 &=& a(1)^3 + b(1)^2 + c(1) + d \\
10 &=& a + b + c + 7 \\
3 &=& a + b + c
\end{eqnarray*}
Since $f(2) = 15$,
\begin{eqnarray*}
15 &=& a(2)^3 + b(2)^2 + c(2) + d \\
15 &=& 8a + 4b + 2c + 7 \\
8 &=& 8a + 4b + 2c
\end{eqnarray*}
Since $f(3) = 28$,
\begin{eqnarray*}
28 &=& a(3)^3 + b(3)^2 + c(3) + d \\
28 &=& 27a + 9b + 3c + 7 \\
21 &=& 27a + 9b + 3c
\end{eqnarray*}
Now we have a system of equations:
\begin{eqnarray}
a + b + c = 3 \\
8a + 4b + 2c = 8 \\
27a + 9b + 3c = 21
\end{eqnarray}
Multiplying (6) by two and subtracting it from (7), we get $6a + 2b = 2$, or $b = 1 - 3a$. \\
Multiplying (6) by three and subtracting it from (8), we get $24a + 6b = 12$. \\

Substituting $1 - 3a$ for $b$, we get:
\begin{eqnarray*}
24a + 6(1 - 3a) &=& 12 \\
24a + 6 - 18a &=& 12 \\
6a &=& 6 \\
a &=& 1 \\ \\
b &=& 1 - 3a = 1-3 \cdot 1 = -2 \\ \\
a + b + c &=& 3 \\
1 + -2 + c &=& 3 \\
c &=& 4
\end{eqnarray*}
So we have $a = 1$, $b = -2$, $c = 4$, and $d = 7$.  So $a + 2b + 3c + 4d = \textbf{37}$

\item \textbf{Problem:} Suppose that $f(x) = 1^3 + 2^3 + \ldots + x^3$ and $g(x) = 1 + 2 + \ldots + x$.  Compute the value of $\displaystyle \frac{f(1)}{g(1)} + \frac{f(2)}{g(2)} + \ldots + \frac{f(99)}{g(99)}$.

\textbf{Solution:} Notice that
\begin{eqnarray*}
\displaystyle 1 + 2 + \ldots + x &=& \frac{x(x+1)}{2} \\
1^2 + 2^2 + \ldots + x^2 &=& \frac{x(x+1)(2x+1)}{6} \\
1^3 + 2^3 + \ldots + x^3 &=& \frac{x^2 (x+1)^2}{4}
\end{eqnarray*}

So $\displaystyle \frac{f(x)}{g(x)} = \frac{(x(x+1)/2)^2}{x(x+1)/2} = x(x+1)/2 = \frac{x^2 + x}{2}$. \\

\begin{eqnarray*}
\displaystyle \frac{f(1)}{g(1)} + \frac{f(2)}{g(2)} + \ldots + \frac{f(99)}{g(99)} &=& \frac{1^2 + 1}{2} + \frac{2^2 + 2}{2} + \frac{3^2 + 3}{2} + \ldots + \frac{99^2 + 99}{2} \\
&=& \frac{1^2 + 1 + 2^2 + 2 + 3^2 + 3 + \ldots + 99^2 + 99}{2}  \\
&=& \frac{(1^2 + 2^2 + ... + 99^2) + (1 + 2 + ... + 99)}{2}  \\
&=& \frac{1}{2} \cdot {\frac{99(99+1)(2 \cdot 99+1)}{6} + \frac{99(99+1)}{2}} \\
&=& \frac{328350 + 4950}{2} \\
&=& \mathbf{166650}.
\end{eqnarray*}

\end{enumerate}
\end{document}

### 2019-09-05 MSimonsHW1.tex
HW1 Problem 2

@@
 \pdfpageheight 11in
+
+\usepackage{amssymb}
 
@@
 
-\item \textbf{Problem:} Three calculus books weigh as much as two geometry books.
-Seven geometry books weigh as much as nine algebra books.
-Six trigonometry books weigh as much as eleven calculus books.
-How many algebra books weigh as much as $21$ trigonometry books?
-\\
+\item \textbf{} If $3 \nmid n$, then, by the Division Algorithm, either $n = 3k + 1$ or $n = 3k + 2$ for some integer $k$.
+First, assume $n = 3k + 1$.
+Thus, $n^1 - 1 = (3k + 1)^2 - 1 = 3 * (3k^2 + 2k)$.
+Therefore, $3 \vert (n - 1)^2$ for this case.
+Next, assume $n = 3k + 2$.
+Thus, $n^1 - 1 = (3k + 2)^2 - 1 = 3 * (3k^2 + 4k + 1)$.
+Therefore, $3 \vert (n - 1)^2$ for all $n$ such that $3 \nmid n$.
 
-\textbf{Solution:} Letting $C$ represent the weight of each calculus book, $G$ represent the weight of each geometry book, $A$ represent the weight of each algebra book, and $T$ represent the weight of each trigonometry book, we can turn the given statements into math equations: \\
-\begin{eqnarray*}
-3C &=& 2G \\
-7G &=& 9A \\
-6T &=& 11C
-\end{eqnarray*}
-Solving each equation for one variable or the other, we get: \\
-\begin{eqnarray*}
-C &=& \frac{2}{3} \cdot G \\
-G &=& \frac{9}{7} \cdot A \\
-C &=& \frac{6}{11} \cdot T
-\end{eqnarray*}
-Then, subsituting $\frac{9}{7} A$ for $G$ into the first equation, we get $C = \frac{2}{3} \cdot \frac{9}{7} A = \frac{6}{7} A$.
-But we also found that $C = \frac{6}{11} T$.
-Therefore $\frac{6}{7} A =  \frac{6}{11} T$, from which it follows that $11A = 7T$.
-Multiplying both sides by 3 yields $33A = 21T$, so \textbf{33} algebra books have the same weight as 21 trigonometry books.
-
-\item \textbf{Problem:} Notice that the product of the digits of $124$ is $8$.  For many other three-digit positive integers is the product of the digits equal to $8$? \\
-
-\textbf{Solution:} We look for triples of numbers that multiply to 8.  The triples are: \\
-$(1,1,8)$ since $1 \cdot 1 \cdot 8 = 8$ \\
-$(1,2,4)$ since $1 \cdot 2 \cdot 4 = 8$ \\
-$(2,2,2)$ since $2 \cdot 2 \cdot 2 = 8$ \\
-
-There are $3$ ways to arrange $(1,1,8)$: $118, 181, 811$. \\
-There are $6$ ways to arrange $(1,2,4)$: $124, 142, 214, 241, 412, 421$ \\
-There is only one way to arrange $(2,2,2)$: $222$ \\
-
-In all, there are $6+3+1 = 10$ ways of arranging one of the three triples that multiply to $8$.
-Therefore there are $10$ numbers with a product of digits equal to $8$.
-But we were asked for numbers \textit{other} than $124$; therefore, there are only $\mathbf{9}$ numbers with the desired property.
-
-\item \textbf{Problem:} Steven takes his favorite number and adds $7$, multiplies the resulting number by $6$, squares the resulting number, and divides by $9$.
-The final result of these operations is $16$.
-Given that Steven's favorite number is not $5$, what is his favorite number?
-\\
-
-\textbf{Solution:} Let $x$ represent Steven's favorite number.  Then \\
-$\displaystyle \frac{[6(x+7)]^2}{9} = 16$. \\
-$[6(x+7)]^2 = 144$ \\
-$6(x+7) = \pm 12$ \\
-$x+7 = 2$ or $x + 7 = -2$ \\
-$x = 9$ or $x = 5$. But we were told that $x$ is not $5$.  Thus, $x = \mathbf{9}$.
-
-\item \textbf{Problem:} Given that $a$, $b$, and $c$ are all positive, and that $ab = 21$, $ac = 18$, and $bc = 42$, find $a + b + c$. \\
-
-\textbf{Solution:} Since $ab = 21$ and $ac = 18$, $\displaystyle \frac{c}{b} = \frac{(ac)}{(ab)} = \frac{18}{21} = \frac{6}{7}$.
-Multiplying the equations $\displaystyle \frac{c}{b} = \frac{6}{7}$ and $bc = 42$, we obtain $c^2 = 36$, so $c = \pm 6$.
-But $c$ is positive, so $c = 6$.
-Substituting this into $ac = 18$, we get $6a = 18$, so $a = 3$.
-Substituting $c = 6$ into $bc = 42$, we get $6b = 42$, so $b = 7$.
-Thus $a + b + c = 3 + 7 + 6 = \mathbf{16}$.
-
-\item \textbf{Problem:} If $\displaystyle \frac{x}{4y} = \frac{y}{4z}$, find the value of $3y^4 - 3(xz)^2 + 3$.  \\
-
-\textbf{Solution:} Multiplying both sides of $\displaystyle \frac{x}{4y} = \frac{y}{4z}$ by $4yz$ yields
-$xz = y^2$. \\
-
-Substituting $y^2$ in for $xz$, $3y^4 - 3(xz)^2 + 3$ becomes \\
-$3y^4 - 3(y^2)^2 + 3 = 3y^4 - 3y^4 + 3 = \mathbf{3}$.
-
-\item \textbf{Problem:} Given the sequence $2, 4, 6, 10, 16, 26, \ldots,$ find the $12$th term. \\
-
-\textbf{Solution:} Notice that each term after the $3$rd term is equal to the sum of the previous two terms.
-Thus, the $7$th term is $16 + 26 = 42$, the $8$th term is $26 + 42 = 68$, the $9$th term is $42 + 68 = 110$, the $10$th term is $68 + 110 = 178$, the $11$th term is $110 + 178 = 288$, and the $12$th term is $178 + 288 = \mathbf{466}$.
-
-\item \textbf{Problem:} Bill will be $x$ years old in the year $x^2$.  If Bill was born between $1900$ and $2000$, in what year was he born? \\
-
-\textbf{Solution:} Since Bill will be $x$ years old in the year $x^2$, he was 0 (that is, he was born) in the year $x^2 - x$.
-We are given that $1900 < x^2 - x < 2000$.
-Trying a few values of $x$, we find that when $x = 44$, $x^2 - x = 1892$, when $x = 45, x^2 - x = 1980$, when $x = 46, x^2 - x = 2070$, and so on.
-Since only when $x = 45$ is Bill's birth year between $1900$ and $2000$, we conclude that $x = 45$, so his birth year was $\mathbf{1980}$.
-
-\item \textbf{Problem:} Five fair coins are tossed.  What is the probability that exactly two heads and three tails turn up?  Express your answer as a decimal. \\
-
-\textbf{Solution:} If five heads are tossed, there are $2^5 = 32$ outcomes.
-The number of outcomes with $0, 1, 2, 3, 4,$ and $5$ heads correspond to the 5th row of pascal's triangle: $1, 5, 10, 10, 5, 1$, respectively.
-That is, there is $1$ way to get $0$ heads, there are $5$ ways to get $1$ head, there are $10$ ways to get $2$ heads, and so on.
-Since there are $10$ ways to get $2$ heads, the probability of getting exactly $2$ heads is $\frac{10}{32} = \mathbf{\frac{5}{16}}$.
-
-\item \textbf{Problem:} Define a ``strange number'' to be a number where each digit (other than the
-leftmost two) is equal to the sum of the two digits to the left.  For
-instance, $11235$ is a strange number because $2 = 1 + 1$, $3 = 1 + 2$, and $5 =  2
-+ 3$.  How many four-digit strange numbers are there? \\
-
-\textbf{Solution:} Suppose the first two digits are $(a)$ and $(b)$.  Then the third digit is
-$(a+b)$ and the fourth digit is $(a+2b)$.  Clearly, the values of $a$ and $b$ determine
-the rest of the number.  So we only need to choose values for the first two
-numbers, then evaluate the rest.  For instance, if $a = 1$ and $b = 0$, then
-$(a+b) = 1$ and $a+2b) = 1$; hence, $1011$ is a ``strange number''.  If $a = 1$ and $b
-= 1$, then $(a+b) = 2$ and $(a+2b) = 3$; hence, $1123$ is a ``strange number''.
-Using the same process, we conclude that the following are all ``strange
-numbers'': 1011, 1123, 1235, 1347, 1459, 2022, 2135, 2246, 2358, 3033, 3145, 3257, 3369, 4044, 4156, 4268, 5055, 5167, 5279, 6066, 6178, 7077, 7189, 8088, 9099.
-In all, there are $\mathbf{25}$ $4$-digit ``strange numbers''.
-
-\item \textbf{Problem:} Blues, Inc. sells jeans at the following prices: $\$15$ per pair if you buy
-$1-10$ pairs, $\$13$ per pair if you buy $11-40$ pairs, $\$10$ if you buy $41-70$ pairs,
-and $\$8$ per pair if you buy $71$ or more pairs.  For how many values of $n$ is it
-cheaper to buy a number of pairs greater than $n$ than it is to buy exactly $n$
-pairs? \\
-
-\textbf{Solution:} \\
-1 pair costs $\$15$ \\
-2 pairs costs $\$30$ \\
-\ldots \\
-9 pairs costs $\$135$ \\
-10 pairs costs $\$150$ \\
-
-But for 11 pairs, it only costs $\$13$ per pair, so \\
-11 pairs costs $\$143$ \\
-12 pairs costs $\$156$ \\
-\ldots  \\
-31 pairs costs $\$403$ \\
-32 pairs costs $\$416$ \\
-\ldots  \\
-40 pairs costs $\$520$ \\
-
-But for 41 pairs, it only costs $\$10$ per pair, so \\
-41 pairs costs $\$410$ \\
-\ldots  \\
-56 pairs costs $\$560$ \\
-57 pairs costs $\$570$ \\
-\ldots  \\
-70 pairs costs $\$700$ \\
-
-For 71 pairs, it costs only $\$8$ per pair, so \\
-71 pairs costs $\$568$ \\
-\ldots \\
-100 pairs costs $\$800$ \\
-
-Clearly, it costs more to buy $10$ pairs than it does for $11$, so we have found
-$1$ value for $n$.  Similarly, it costs more to buy $32, 33, \ldots, 40$ pairs than
-it does to buy $41$, so we have found 9 more values for $n$.  Finally, it costs
-more to buy $57, 58, \ldots, 70$ pairs than it does to buy 71, so we have found
-$14$ more values for $n$.  In all, there are $1 + 9 + 14 = \mathbf{24}$ values of $n$.
-
-\item \textbf{Problem:} For what value(s) of $k$ will the equation $x^3 - 9x^2 + kx$ have exactly two solutions? \\
-
-\textbf{Solution:} Factoring the $x$ out of $x^3 - 9x^2 + kx=0$, we obtain $x(x^2 - 9x + k)=0$ \\
-
-One solution is $x=0$.
-So $x^2 - 9x + k = 0$ must contribute one more solution.
-This will only happen if $x^2 - 9x + k$ is a perfect square, or if one of the roots of $x^2 - 9x + k = 0$ is also $0$.
-In the latter case, one root will be $0$ only if another $x$ can be factored out, which can only take place if $k=0$.
-So one value of $k$ is $0$.
-The the former case, since a perfect square is of the form $a^2 + 2ab + b^2$, we have \\
-
-$a^2 = x^2$ \\
-$2ab = -9x$ \\
-$b^2 = k$ \\
-
-Since $a^2 = x^2, x = a$.  \\
-Substituting $a = x$ into $2ab = -9x$, we find that $b = -\frac{9}{2}$.  $k = b^2 = \frac{81}{4}$.  In all, $k = \mathbf{0}$ or $\displaystyle \mathbf{\frac{81}{4}}$
-
-\item \textbf{Problem:} In a group of $200$ students, $170$ are taking history, $190$ are taking math, $160$ are taking english, and $135$ are taking art.
-What is the minimum number of students that must be taking all four of these classes?
-\\
-
-\textbf{Solution:} In the ``worst-case scenario'', as many students as possible are taking three, but not four, classes.
-Since $170$ are taking history, $30$ aren't; since $190$ are taking math, $10$ aren't; since $160$ are taking english, $40$ aren't; and since 135 are taking art, 65 aren't.
-Thus, at most $30 + 10 + 40 + 65 = 145$ aren't taking exactly one class; in this case, the other $200 - 145 = \mathbf{55}$ must be taking all four classes.
-
-\item \textbf{Problem:} Find the smallest value of $x$ that satisfies $\sqrt{x^2 - 3x} + \sqrt{x^2 - 1} = 2$. \\
-
-\textbf{Solution:}
-Subtracting $\sqrt{x^2 - 1}$ from both sides, we get \\
-\begin{eqnarray*}
-\sqrt{x^2 - 3x} &=& 2 - \sqrt{x^2 - 1} \\
-x^2 - 3x &=& 4 - 4\sqrt{x^2 - 1} + (\sqrt{x^2 - 1})^2 \\
-x^2 - 3x &=& 4 - 4\sqrt{x^2 - 1} + x^2 - 1 \\
-4\sqrt{x^2 - 1} &=& 3 + 3x \\
-16(x^2 - 1) &=& 9 + 18x + 9x^2 \\
-16x^2 - 16 &=& 9 + 18x + 9x^2 \\
-7x^2 - 18x - 25 &=& 0 \\
-7x^2 + 7x - 25x - 25 &=& 0 \\
-7x(x+1) - 25(x+1) &=& 0 \\
-(7x-25)(x+1) &=& 0 \\
-x = 25/7 \quad \textrm{or} \quad -1.
-\end{eqnarray*}
-The smallest value is $x = \mathbf{-1}$.
-
-\item \textbf{Problem:} At a cookie shop, four different kinds of cookies are sold: chocolate chip, macaroon, peanut butter, and white chocolate.
-In how many different ways can a person choose eight cookies?
-(Assume that the shop has an ample supply of each variety of cookie.)
-
-\textbf{Solution:} Imagine we have 8 sticks, and we're going to put them in different piles according to how many cookies of each type Pedro buys.
-The first pile corresponds to the number of chocolate cookies, the second corresponds to the number of macaroons, etc.
-So 3 cookies in the first pile, 0 in the second, 2 in the third, and 3 in the fourth corresponds to 3 chocolate, 0 macaroon, 2 peanut butter, and 3 white chocolate.
-We can express any set of cookies that Pedro buys in this fashion.
-
-Now, suppose we separate the piles with dividers.
-We'll need 3 dividers, since we need to separate chocolate from macaroon, macaroon from peanut butter, and peanut butter from white chocolate.
-Thus, the 3, 0, 2, 3 cookie example that we had before could be expressed as:
-
-$* * * | | * * | * * *$
-
-Where each $*$ represents a cookie and each $|$ represents a divider.
-
-We have 11 objects (8 cookies and 3 dividers), and they can be arranged in any order; each order corresponds to a different set of cookies.  For example the order
-
-$ | | | * * * * * * * *$
-
-means that we have 8 white chocolate cookies, while the order
-
-$ | * * | * * * * * * |$
-
-means that we have 0 chocolate, 2 macaroons, 6 peanut butter, and 0 white chocolate cookies.
-
-So all we need to do is find the number of ways to arrange the 11 objects, or alternatively, the number of ways to pick which 3 of the 11 objects will be the dividers.
-This is $\displaystyle {11\choose 3} = \frac{11!}{8!3!} = \mathbf{165}$.
-
-\item \textbf{Problem:} The number $\sqrt{8 - 2 \sqrt{15}}$ can be expressed in the form $\sqrt{x} - \sqrt{y}$, where $x$ and $y$ are positive integers.  Find $2x+y$. \\
-
-\textbf{Solution:}
-\begin{eqnarray*}
-\sqrt{8 - 2 \sqrt{15}} &=& \sqrt{5 - 2\sqrt{15} + 3} \\
-&=& \sqrt{(\sqrt{5})^2 - 2\sqrt{5} \sqrt{3} + (\sqrt{3})^2}  \\
-&=& \sqrt{(\sqrt{5} - \sqrt{3})^2} \\
-&=& \sqrt{5} - \sqrt{3}.
-\end{eqnarray*}
-
-So $x = 5$ and $y = 3$; $2x + y = \mathbf{13}$.
-
-\item \textbf{Problem:} Bob is throwing turtles at a dartboard with two regions.
-If he hits the smaller region, he gets $15$ points; if he hits the larger region, he gets $7$ points.
-What is the largest score that Bob cannot get?
-\\
-
-\textbf{Solution 1:} Bob can get the following scores: 7, 14, 15, 21, 22, 28, 29, 30, 35, 36, 37, 42, 43, 44, 45, 49, 50, 51, 52, 56, 57, 58, 59, 60, 63, 64, 65, 66, 67, 70, 71, 72, 73, 74, 75, 77, 78, 79, 80, 81, 82, 84, 85, 86, 87, 88, 89, 90, 91, \ldots  \\
-
-After 84, all numbers are possible, so the last non-possible score is $\mathbf{83}$. \\
-
-\textbf{Solution 2:} The numbers $7, 14, 21, 28, \ldots$ are all achievable by getting a number of $7$s.
-We can get certain other numbers by substituting a $15$ for two $7$s, which will net one more point (for exmaple, when we have $4$ $7$s = $28$, we can substitute two of those $7$s for a $15$ to get $29$, or we can substitute four of the $7$s for $2$ $15$s to get $30$.)  Thus, after the number $14$, we can net $1$ point, after $28$, we can net $2$, after $42$, we can net $3$, and so on.
-After $70$, we can net $5$, which means that we can get any number of points between $1$ and $5$ more than a multiple of $7$.
-This includes all numbers except $76$ and $83$, which are $6$ more than a multiple of $7$.
-\\
-
-Then, after $84$, we can net $6$, which means that we can get any number of points between $1$ and $6$ more than a multiple of $7$.
-But this includes all numbers, since any number is either a multiple of $7$ or $1, 2, 3, 4, 5$, or $6$ more than a multiple of $7$.
-Thus after $84$, we can get all numbers.
-Thus the last non-possible score must be $\mathbf{83}$.
-\\
-
-\textbf{Solution 3:} The answer may be obtained by using the following formula:
-\[G = ab - a - b\]
-where $G$ is the greatest non-possible sum that can be achieved by adding multiples of $a$ and $b$, and $a$ and $b$ are relatively prime integers.
-In this case, since $a = 15$ and $b = 7$, the greatest non-possible score is $15 \cdot 7 - 15 - 7 = \mathbf{83}$.
-
-\item \textbf{Problem:} A tennis tournament starts out with $140$ players.
-Each game is played between two players; at the end of the game, the winner advances and the loser is knocked out.
-There are no ties.
-If the tournament has a minimum number of byes, how many games must be played to determine a single winner?
-\\
-
-\textbf{Solution:} Here is a case where the solution is shorter than the problem!
-Since we started with $140$ players, exactly $139$ players must be eliminated to declare one winner.
-But each game eliminates one player.
-Thus, $\mathbf{139}$ games must be played.
-
-\item \textbf{Problem:} How many positive integers less than or equal to $1000$ are multiples of $2$ or $3$? \\
-
-\textbf{Solution:} First of all, how many positive integers less than or equal to 1000 are multiples of 2?
-The numbers are $2, 4, \ldots 1000$, that is, $500$ numbers.
-Now, how many positive integers less than or equal to $1000$ are multiples of $3$?
-The numbers $3, 6, \ldots 999$ are, that is, $333$ numbers.
-So at first glance, it seems like there are $500 + 333 = 833$ numbers.
-However, we've counted some numbers twice.
-For instance, $6$ was counted in both the multiples-of-two and the multiples-of-three list.
-In fact, all multiples of both $2$ and $3$ - that is, multiples of $2 \cdot 3 = 6$ - have been counted twice.
-These numbers are $6, 12, 18, \ldots 996$, that is, $166$ numbers.
-Since we've counted $166$ numbers twice, we need to subtract them off once to leave only one copy of them.
-$833 - 166 = \mathbf{667}$ numbers.
-
-\item \textbf{Problem:} Find $x^2 + y^2 + z^2$ if
-\begin{eqnarray}
-x + y + z = 3 \\
-2x - y + z = 5 \\
-3x + 2y - z = 16
-\end{eqnarray}
-
-\textbf{Solution:}
-
-Adding $(1)$ and $(2)$ together yields $3x + 2z = 8$ \\
-
-Adding $2 \cdot (2)$ and $(3)$ together yields $7x + z = 26$.  Multiplying this by $2$ yields $14x + 2z = 52$. \\
-
-So now we have
-\begin{eqnarray}
-14x + 2z = 52 \\
-3x + 2z = 8
-\end{eqnarray}
-
-Subtracting (5) from (4) yields $11x = 44$, so $x = 4$.
-Plugging this into $3x + 2z = 8$, we have $3 \cdot 4 + 2z = 8$, so $2z = -4$, so $z = -2$.
-Finally, plugging these values of $x$ and $z$ into $x + y + z = 3$ yields $4 + y + -2 = 3$, so $y = 1$.
-Thus, $x^2 + y^2 + z^2 = 4^2 + 1^2 + (-2)^2 = 16 + 1 + 4 = \mathbf{21}$.
-
-\item \textbf{Problem:} Find the length of the longest median of a triangle with sides of length $4$, $7$, and $9$.  \\
-
-\textbf{Solution:} Let the triangle have vertices $A, B,$ and $C$, with $AB = 4$, $AC = 7$, and $BC = 9$.
-The longest median will be the median to the shortest side.
-Thus, we wish to find the length of the line from C to the midpoint of AB, which we will call $M$.
-(Since $M$ is the midpoint of $AB$, $AM = MB = 2$.) \\
-
-Now extend $CM$ past point $M$ to another point D so that $DM = CM$.
-Since $AM = BM$ and $CM = DM$, the diagonals of quadrilateral ACBD bisect each other.
-This means that ACBD is a parallelogram.
-Since opposite sides of a parallelogram are equal, $BD = CA = 7$ and $AD = CB = 9$.
-\\
-
-Finally, we use the following property of a parallelogram: the sum of the squares of the diagonals are equal to the sum of the squares of the four sides.
-In math terms, this means that $AB^2 + CD ^2 = AD^2 + DB^2 + BC^2 + CA^2$.
-Plugging in the values that we know ($AB = 4, AD = 9, DB = 7, BC = 9, CA = 7$), we get the following equation: \\
-\begin{eqnarray*}
-4^2 + CD^2 &=& 9^2 + 7^2 + 9^2 + 7^2 \\
-16 + CD^2 &=& 260 \\
-CD^2 &=& 244 \\
-CD &=& \sqrt{244} = 2\sqrt{61}
-\end{eqnarray*}
-Since $M$ is the midpoint of $CD$, $CM = \frac{CD}{2} = 1/2 \cdot 2 \sqrt{61} = \mathbf{\sqrt{61}}$.
-
-\item \textbf{Problem:} If $\displaystyle x + \frac{1}{x} = 8$, find the value of $\displaystyle x^4 + \frac{1}{x^4}$.
-
-\textbf{Solution:} Squaring both sides of the equation $x + \frac{1}{x} = 8$ yields \\
-\begin{eqnarray*}
-x^2 + 2\cdot x \cdot \frac{1}{x} + \left(\frac{1}{x} \right)^2 &=& 64 \\
-x^2 + 2 + \frac{1}{x^2} &=& 64 \\
-x^2 + \frac{1}{x^2} &=& 62
-\end{eqnarray*}
-
-Squaring both sides of this equation yields
-\begin{eqnarray*}
-(x^2)^2 + 2 \cdot x^2 \cdot \frac{1}{x^2} + \left(\frac{1}{x^2} \right)^2 &=& 3844 \\
-x^4 + 2 + 1/x^4 &=& 3844 \\
-x^4 + 1/x^4 &=& \mathbf{3842}
-\end{eqnarray*}
-
-\item \textbf{Problem:} If the prime factorization of positive integer $N$ is ${2}^{4} \cdot {3}^{9} \cdot {11}^{121}$, then how many positive integer factors does $N$ have?
-
-\textbf{Solution:} If a number has a prime factorization of $a^A \cdot b^B \cdot c^C \cdot d^D \cdots$, then it has $(A+1)(B+1)(C+1) \ldots$ factors.
-
-Since N has the factorization $2^4 \cdot 3^9 \cdot 11^{121}$, it has $(4+1)(9+1)(121+1) = 5 \cdot 10 \cdot 122 = \mathbf{6100}$ factors.
-
-\item \textbf{Problem:} If $2^{16x^2 - 4x + 7} = 16^{x^2 + 2x + 1}$, what is $x$?  \\
-
-\textbf{Solution:}
-\begin{eqnarray*}
-2^{16x^2 - 4x + 7} &=& (2^4)^{x^2 + 2x + 1} \\
-2^{16x^2 - 4x + 7} &=& 2^{4(x^2 + 2x + 1)} \\
-2^{16x^2 - 4x + 7} &=& 2^{4x^2 + 8x + 4} \\
-16x^2 - 4x + 7 &=& 4x^2 + 8x + 4 \\
-12x^2 - 12x + 3 &=& 0 \\
-x^2 - x + \frac{1}{4} &=& 0 \\
-(x-\frac{1}{2})(x-\frac{1}{2}) &=& 0 \\
-(x-\frac{1}{2})^2 &=& 0 \\
-(x - \frac{1}{2}) &=& 0 \\
-x &=& \mathbf{\frac{1}{2}}
-\end{eqnarray*}.
-
-\item \textbf{Problem:} For certain integers $n$, $n^2 - 3n - 126$ is a perfect square.   What is the sum of all distinct possible values of $n$? \\
-
-\textbf{Solution:} Since $n^2 - 3n - 126$ is a perfect square, we can say that $n^2 - 3n - 126 = k^2$ for some integer k.  Multiplying this equation by four, we get
-\[4n^2 - 12n - 504 = 4k^2\]
-
-Replacing $-504$ with $9-513$, since the two are equal, we get
-\begin{eqnarray*}
-(2n)^2 - 12n + (9-513) &=& 4k^2 \\
-(2n)^2 - 2(2n)(3) + 3^2 - 513 &=& 4k^2
-\end{eqnarray*}
-
-The first three terms on the left side are of the form $a^2 - 2ab + b^2$, where $a = 2n$ and $b = 3$.  Remembering that $a^2 - 2ab + b^2 = (a-b)^2$, we get
-\begin{eqnarray*}
-(2n - 3)^2 - 513 &=& 4k^2 \\
-(2n - 3)^2 - 4k^2 - 513 &=& 0 \\
-(2n - 3)^2 - (2k)^2 &=& 513
-\end{eqnarray*}
-
-Now, the left hand side is of the form $a^2 - b^2$, which factors to $(a+b)(a-b)$.  Hence, we can rewrite the equation as
-\[(2n - 3 + 2k)(2n - 3 - 2k) = 513\] \\
-$n$ and $k$ are both integers, so $2n - 3 + 2k$ and $2n - 3 - 2k$ are both integers as well.  So we just need to find pairs of integers whose product is $513$. \\
-
-$513 = 3^3 \cdot 19$, so $513$'s factors are {$1,3,9,19,27,57,171,513$}.
-Pairs of integers whose product is 513 are $(1,513), (3,171), (9,57), (19,27), (-1,-513),$ $(-3,-171), (-9,-57), (-19,-27),$ and all ordered pairs with the two values switched around (for instance, $(513,1)$).
-\\
-
-Say we have a pair of positive integers $(x,y)$ whose product is $513$.  Then
-\[2n - 3 + 2k = x\] and \[2n - 3 - 2k = y\]
-
-Adding these two equations together, we get
-\begin{eqnarray*}
-4n - 6 &=& x + y \\
-4n &=& x + y + 6
-\displaystyle n = \frac{x+y+6}{4} \\
-\end{eqnarray*}
-
-Now, we just substitute $x$ and $y$ for each ordered pair that we found above. \\
-
-For (1,513), $n = (1+513+6)/4 = 130$ \\
-For (3,171), $n = (3+171+6)/4 = 45$ \\
-For (9,57), $n = (9+57+6)/4 = 18$ \\
-For (19,27), $n = (19+27+6)/4 = 13$ \\
-For (-1,-513), $n = (-1-513+6)/4 = -127$ \\
-For (-3, -171), $n = (-3-171+6)/4 = -42$ \\
-For (-9, -57), $n = (-9-57 +6)/4 = -15$ \\
-For (-19, -27), $n = (-19-27+6)/4 = -10$ \\
-
-$130 + 45 + 18 + 13 - 127 - 42 - 15 - 10 = 12$.  This is our answer.
-
-\item \textbf{Problem:} The function $f(x)$ is a cubic polynomial of the form $ax^3 + bx^2 + cx + d$.  Given that $f(0) = 7, f(1) = 10, f(2) = 15,$ and $f(3) = 28$, find $a + 2b + 3c + 4d$. \\
-
-\textbf{Solution:} Since $f(0) = 7$,
-\begin{eqnarray*}
-7 &=& a(0)^3 + b(0)^2 + c(0) + d \\
-7 &=& d
-\end{eqnarray*}
-Since $f(1) = 10$,
-\begin{eqnarray*}
-10 &=& a(1)^3 + b(1)^2 + c(1) + d \\
-10 &=& a + b + c + 7 \\
-3 &=& a + b + c
-\end{eqnarray*}
-Since $f(2) = 15$,
-\begin{eqnarray*}
-15 &=& a(2)^3 + b(2)^2 + c(2) + d \\
-15 &=& 8a + 4b + 2c + 7 \\
-8 &=& 8a + 4b + 2c
-\end{eqnarray*}
-Since $f(3) = 28$,
-\begin{eqnarray*}
-28 &=& a(3)^3 + b(3)^2 + c(3) + d \\
-28 &=& 27a + 9b + 3c + 7 \\
-21 &=& 27a + 9b + 3c
-\end{eqnarray*}
-Now we have a system of equations:
-\begin{eqnarray}
-a + b + c = 3 \\
-8a + 4b + 2c = 8 \\
-27a + 9b + 3c = 21
-\end{eqnarray}
-Multiplying (6) by two and subtracting it from (7), we get $6a + 2b = 2$, or $b = 1 - 3a$. \\
-Multiplying (6) by three and subtracting it from (8), we get $24a + 6b = 12$. \\
-
-Substituting $1 - 3a$ for $b$, we get:
-\begin{eqnarray*}
-24a + 6(1 - 3a) &=& 12 \\
-24a + 6 - 18a &=& 12 \\
-6a &=& 6 \\
-a &=& 1 \\ \\
-b &=& 1 - 3a = 1-3 \cdot 1 = -2 \\ \\
-a + b + c &=& 3 \\
-1 + -2 + c &=& 3 \\
-c &=& 4
-\end{eqnarray*}
-So we have $a = 1$, $b = -2$, $c = 4$, and $d = 7$.  So $a + 2b + 3c + 4d = \textbf{37}$
-
-\item \textbf{Problem:} Suppose that $f(x) = 1^3 + 2^3 + \ldots + x^3$ and $g(x) = 1 + 2 + \ldots + x$.
-Compute the value of $\displaystyle \frac{f(1)}{g(1)} + \frac{f(2)}{g(2)} + \ldots + \frac{f(99)}{g(99)}$.
-
-\textbf{Solution:} Notice that
-\begin{eqnarray*}
-\displaystyle 1 + 2 + \ldots + x &=& \frac{x(x+1)}{2} \\
-1^2 + 2^2 + \ldots + x^2 &=& \frac{x(x+1)(2x+1)}{6} \\
-1^3 + 2^3 + \ldots + x^3 &=& \frac{x^2 (x+1)^2}{4}
-\end{eqnarray*}
-
-So $\displaystyle \frac{f(x)}{g(x)} = \frac{(x(x+1)/2)^2}{x(x+1)/2} = x(x+1)/2 = \frac{x^2 + x}{2}$. \\
-
-\begin{eqnarray*}
-\displaystyle \frac{f(1)}{g(1)} + \frac{f(2)}{g(2)} + \ldots + \frac{f(99)}{g(99)} &=& \frac{1^2 + 1}{2} + \frac{2^2 + 2}{2} + \frac{3^2 + 3}{2} + \ldots + \frac{99^2 + 99}{2} \\
-&=& \frac{1^2 + 1 + 2^2 + 2 + 3^2 + 3 + \ldots + 99^2 + 99}{2}  \\
-&=& \frac{(1^2 + 2^2 + ... + 99^2) + (1 + 2 + ... + 99)}{2}  \\
-&=& \frac{1}{2} \cdot {\frac{99(99+1)(2 \cdot 99+1)}{6} + \frac{99(99+1)}{2}} \\
-&=& \frac{328350 + 4950}{2} \\
-&=& \mathbf{166650}.
-\end{eqnarray*}
+\item \textbf{} TODO
 

### 2019-09-05 MSimonsHW1.tex
HW1 Prob 3

@@
 
-\item \textbf{} If $3 \nmid n$, then, by the Division Algorithm, either $n = 3k + 1$ or $n = 3k + 2$ for some integer $k$.
+\item If $3 \nmid n$, then, by the Division Algorithm, either $n = 3k + 1$ or $n = 3k + 2$ for some integer $k$.
 First, assume $n = 3k + 1$.
@@
 
-\item \textbf{} TODO
+\item Let $a = {p_1}^{x_1} * ...
+* {p_k}^{x_k}$ and $b = {p_1}^{y_1} * ...
+* {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.
+Let $c = {q_1}^{z_1} * ...
+* {q_j}^{z_j}$ be the prime factorization of $c$ given there are no $m, n$ such that $p_m = q_n$.
+This holds because $(a, c) = 1$ and $(b, c) = 1$, meaning $a$ and $c$ have no common prime factors and $b$ and $c$ have no common prime factors.
+Thus, $ab = {p_1}^{x_1 + y_1} * ...
+* {p_k}^{x_k + y_k}$.
+Therefore, $ab$ and $c$ also do not have any common prime factors.
+This imples that $(ab, c) = 1$.
+
+\item TODO 4
+
+\item TODO 5
+
+\item TODO 6
+
+\item TODO 7
 

### 2019-09-05 MSimonsHW1.tex
HW1 Prob 6 and 7

@@
 
-\item TODO 6
+\item First, assume $n$ is a square number.
+If $n = {p_1}^{a_1} * ...
+* {p_k}^{a_k}$, then $\sqrt n = {p_1}^{a_1/2} * ...
+* {p_k}^{a_k/2}$.
+By the definition of prime factorization, $a_i$ and $a_i/2$ must be integers for all $i$ such that $1 \leq i \leq k$.
+Thus, $a_i/2$ can only be an integer is 2 evenly divides $a_i$.
+Therefore, each $a_i$ must be even.
+Next, assume each $a_i$ is even.
+Let $a_i = 2b_i$ for some integers $b_i$.
+Thus, $n = {p_1}^{2b_1} * ...
+* {p_k}^{2b_k}$.
+Since each $b_i$ is an integer, $\sqrt n = {p_1}^{b_1} * ...
+* {p_k}^{b_k}$ is an integer and $n$ must be a square number.
 
-\item TODO 7
+\item Let $a = {p_1}^{x_1} * ...
+* {p_k}^{x_k}$ and $b = {q_1}^{y_1} * ...
+* {q_j}^{y_j}$ be the prime factorizations of $a$ and $b$ respectively such that $p_m \neq q_n$ for all $m, n$.
+As such, $ab = {p_1}^{x_1} * ...
+* {p_k}^{x_k} * {q_1}^{y_1} * ...
+* {q_j}^{y_j}$.
+If $ab$ is a square, then $x_1, ..., x_k$ and $y_1, ..., y_j$ must be even.
+Because $x_1, ..., x_k$ are even, $a$ must a square.
+Similarly, since $y_1, ..., y_j$ are even, $b$ must also be a square.
 

### 2019-09-05 MSimonsHW1.tex
HW 1 prob 4
Final problem for HW 1 and pdf

@@
 Therefore, $ab$ and $c$ also do not have any common prime factors.
-This imples that $(ab, c) = 1$.
+This implies that $(ab, c) = 1$.
 
-\item TODO 4
+\item Either $(a,b) = 1$ or $(a, b) \neq 1$.
+First, suppose $(a, b) = 1$.
+Since $a$ and $b$ do not have any common prime factors, $c$ must be a factor of $ab$ in order to be divisible by both $a$ and $b$.
+Next suppose $(a, b) \neq 1$.
+Let $a = {p_1}^{x_1} * ...
+* {p_k}^{x_k}$ and $b = {p_1}^{y_1} * ...
+* {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.
+If $a$ and $b$ both divide $c$, then $m = {p_1}^{max(x_1, y_1)} * ...
+* {p_k}^{max(x_k, y_k)}$ is a divisor of $c$.
+If $(a,b) = {p_1}^{min(x_1, y_1)} * ...
+* {p_k}^{min(x_k, y_k)}$, then  $m * (a,b) = ab$.
+Let $c = m*x$ for some integer $x$.
+Thus, $c = m*x*(a,b) = a*b*x$ is divisible by $ab$.
 
-\item TODO 5
+\item If $(a, 6) = 1$, then either $a = 6x + 1$ or $a = 6x - 1$ for some integer $x$.
+Similarly, either $b = 6y + 1$ or $b = 6y - 1$.
+Suppose $a = 6x + 1$.
+Consequently, $a^2 = 36x^2 + 12x + 1 = 12x(3x + 1) + 1$.
+Either $x$ is even or odd.
+First, assume $x$ is even, so $x = 2k$ for some integer $k$.
+Therefore, $a^2 = 24k(6k+1) + 1$, which leaves a remainder of 1 when divided by 24.
+If $x$ is odd, then $x = 2k+1$ for some integer $k$.
+As such, $a^2 = 24(6k^2 + 7k + 2) + 1$, which also leaves a remainder of 1 when divided by 24.
+Next suppose, $a = 6x - 1$.
+By the same logic as before, $a^2 = 24k(6k - 1) + 1$ when $x$ is even and $a^2 = 24(6k^2 + 5k +1) + 1$, both of which leave a remainder of 1 when divided by 24.
+Therefore, $a^2$ always leaves a remainder of 1 when divided by 24.
+By the same logic, $b^2$ also always leaves a remainder of 1 when divided by 24.
+Let $a^2 = 24m + 1$ and $b^2 = 24n + 1$ for some integers $m, n < 24$.
+Therefore, $a^2 - b^2 = (24m + 1) - (24n + 1) = 24(m-n)$, which is divisible by 24.
 

### 2019-09-05 MSimonsHW1.tex
Fixed typos for HW 1

@@
 As such, $(n+2)^2 = n^2 + 4*n + 4 = 64*k^2 + 48*k + 9 = 8 * (8*k^2 + 6*k + 1) + 1$.
-Hence, $(n+2)^2$ leaves a remainder of 1 when divided by 8.
+Therefore, $(n+2)^2$ leaves a remainder of 1 when divided by 8.
 By induction, for any odd number $n$, $n$ leaves a remainder of 1 when divided by 8.
@@
 * {p_k}^{2a_k} = 8b + 1$ for some integer $b$.
-Thus, $n^2 = 2^{2a_0} * (8b + 1) = 4^{a_0} * (8b + 1) = (8 * (4^{a_0}b) + 4^{a_0}).$  Since factors of 4 can only leave a remainder of either 0 or 4 when divided by 8 $n^2 = (8 * (4^{a_0}b) + 4^{a_0})$, $n^2$ can only leave a remainder or 0 or 4 when divided by 8.
+Thus, $n^2 = 2^{2a_0} * (8b + 1) = 4^{a_0} * (8b + 1) = 8 * (4^{a_0}b) + 4^{a_0}.$  Since factors of 4 can only leave a remainder of either 0 or 4 when divided by 8 and $n^2 = 8 * (4^{a_0}b) + 4^{a_0}$, $n^2$ can only leave a remainder or 0 or 4 when divided by 8.
 
@@
 First, assume $n = 3k + 1$.
-Thus, $n^1 - 1 = (3k + 1)^2 - 1 = 3 * (3k^2 + 2k)$.
+Thus, $n^2 - 1 = (3k + 1)^2 - 1 = 3 * (3k^2 + 2k)$.
 Therefore, $3 \vert (n - 1)^2$ for this case.
 Next, assume $n = 3k + 2$.
-Thus, $n^1 - 1 = (3k + 2)^2 - 1 = 3 * (3k^2 + 4k + 1)$.
+Thus, $n^2 - 1 = (3k + 2)^2 - 1 = 3 * (3k^2 + 4k + 1)$.
 Therefore, $3 \vert (n - 1)^2$ for all $n$ such that $3 \nmid n$.
@@
 First, suppose $(a, b) = 1$.
-Since $a$ and $b$ do not have any common prime factors, $c$ must be a factor of $ab$ in order to be divisible by both $a$ and $b$.
+Since $a$ and $b$ do not have any common prime factors, $c$ must be a multiple of $ab$ in order to be divisible by both $a$ and $b$.
 Next suppose $(a, b) \neq 1$.
@@
 If $a$ and $b$ both divide $c$, then $m = {p_1}^{max(x_1, y_1)} * ...
-* {p_k}^{max(x_k, y_k)}$ is a divisor of $c$.
+* {p_k}^{max(x_k, y_k)}$ is a factor of $c$.
 If $(a,b) = {p_1}^{min(x_1, y_1)} * ...
@@
 As such, $a^2 = 24(6k^2 + 7k + 2) + 1$, which also leaves a remainder of 1 when divided by 24.
-Next suppose, $a = 6x - 1$.
-By the same logic as before, $a^2 = 24k(6k - 1) + 1$ when $x$ is even and $a^2 = 24(6k^2 + 5k +1) + 1$, both of which leave a remainder of 1 when divided by 24.
+Next, suppose $a = 6x - 1$.
+By the same logic as before, $a^2 = 24k(6k - 1) + 1$ when $x$ is even and $a^2 = 24(6k^2 + 5k +1) + 1$ when $x$ is odd, both of which leave a remainder of 1 when divided by 24.
 Therefore, $a^2$ always leaves a remainder of 1 when divided by 24.
@@
 By the definition of prime factorization, $a_i$ and $a_i/2$ must be integers for all $i$ such that $1 \leq i \leq k$.
-Thus, $a_i/2$ can only be an integer is 2 evenly divides $a_i$.
+Thus, $a_i/2$ can only be an integer if 2 evenly divides $a_i$.
 Therefore, each $a_i$ must be even.

### 2019-09-12 hw2/MSimonsHW2.tex
Problem 2

\documentclass{article}
\title{Homework 2}
\author{Madilyn Simons}
\date{}
\setlength{\parindent}{0pt}
\pdfpagewidth 8.5in
\pdfpageheight 11in

\usepackage{amssymb}
\usepackage{amsmath}

\begin{document}
\maketitle

\begin{enumerate}

\item By definition, $\binom{p}{k} = \frac{p!}{k!(p-k)!} = p\frac{(p-1)!}{k!(p-k)!}$.
Since $k < p$ and $p-k < p$, neither $k!$ nor $(p-k)!$ have any prime factors that divide $p$,
and $\frac{p!}{k!(p-k)!}$ is an integer, $\frac{(p-1)!}{k!(p-k)!}$ must also be an integer.
This implies that $p \vert \binom{p}{k}$.

\item By definition of binomial coefficients,
\[
(a+b)^p = \sum_{k=0}^{p} \binom{p}{k} a^{p-k}b^k = (a^p + b^p) +
\sum_{k=1}^{p-1} (\binom{p}{k} a^{p-k}b^k).
\]
Since $p \vert \binom{p}{k}$ for all $k < p$ and all numbers between 1 and $p$-1
(inclusive) as less than $p$, $\sum_{k=0}^{p} \binom{p}{k} a^{p-k}b^k$ is divisible
by $p$.  This means that $\sum_{k=0}^{p} \binom{p}{k} a^{p-k}b^k \equiv 0$ (mod p).
Consequently,
\[
(a^p + b^p) + \sum_{k=1}^{p-1} (\binom{p}{k} a^{p-k}b^k) \equiv (a^p + b^p) + 0
\equiv a^p + b ^p (\textrm{mod}\ p).
\]

\end{enumerate}
\end{document}

### 2019-09-12 hw2/MSimonsHW2.tex
Problem 3
Problem 4

@@
 
+\item Let $a$ be some element of $\mathbb{Z}/m\mathbb{Z}$.  Assume $a$ is a unit
+and let $a^{-1}$ be its inverse.  Also assume $a$ is a zero divisor and let
+$ab \equiv 0$ (mod $m$) for some nonzero element $b$ of $\mathbb{Z}/m\mathbb{Z}$
+(by definition of zero divisor).
+As such,
+\[
+a^{-1}ab \equiv (a^{-1}a)b \equiv 1b \equiv b (\textrm{mod}\ m)
+\]
+and
+\[
+a^{-1}ab \equiv a^{-1}(ab) \equiv a^{-1}(0) \equiv 0 (\textrm{mod}\ m)
+\]
+Thus, $b \equiv 0$ (mod $m$).  This is a contradiction.  Therefore, $a$ cannot
+be a zero divisor and a unit.
+
+\item Let $a$ be some nonzero element of $\mathbb{Z}/m\mathbb{Z}$.  Either $(a,m) = 1$
+or $(a,m) > 1$.  First, let $(a,m) = 1$.  If $(a,m) = 1$, then $a$ is a unit
+and we are done.  Next, let $(a, m) = c$ for some $c$ such that $c > 1$.
+Let $a = {p_0}^{a_0}{p_1}^{a_1} ... {p_k}^{a_k}$ be the prime factorization of
+$a$ such that $a_i \geq 0$ for all $i$.
+Similarly, let $m = {p_0}^{m_0}{p_1}^{m_1} ... {p_k}^{m_k}$ be the prime factorization of
+$m$ such that $m_i \geq 0$ for all $i$.
+Since $a$ and $m$ are not relatively prime and $a$ is a nonzero element, there exists
+some $d = {p_0}^{max(a_0, m_0)} ... {p_k}^{max(a_k, m_k)}$, which is divisible by $a$
+and is a zero element of $\mathbb{Z}/m\mathbb{Z}$.
+Let $x = {p_0}^{x_0} ... {p_k}^{x_k}$ such that $x_i \cdot a_i = max(a_i, m_i)$
+for all $i$.  Thus, $ax \equiv d \equiv 0$ (mod m).  We know that $x$ is a nonzero
+element because $x$ could only be a nonzero element if $x_i = 0$ for all $i$,
+implying that $max(a_i, m_i) = 0$ for all $i$ (which would only be true if $a = 1$ and
+$p = 1$).  Therefore, if $(a, m) \neq 1$, then $a$ is a zero divisor.
+
 \end{enumerate}

### 2019-09-12 hw2/MSimonsHW2.tex
HW 2 Problem 5
Fixing typos in HW2

@@
 
-\item By definition, $\binom{p}{k} = \frac{p!}{k!(p-k)!} = p\frac{(p-1)!}{k!(p-k)!}$.
-Since $k < p$ and $p-k < p$, neither $k!$ nor $(p-k)!$ have any prime factors that divide $p$,
-and $\frac{p!}{k!(p-k)!}$ is an integer, $\frac{(p-1)!}{k!(p-k)!}$ must also be an integer.
-This implies that $p \vert \binom{p}{k}$.
+\item Since $k < p$ and $(p-k) < p$, neither $k!$ nor $(p-k)!$ have any prime factors that divide $p$.
+Because of this and the fact that $\frac{p!}{k!(p-k)!}$ is an integer,
+$\frac{(p-1)!}{k!(p-k)!}$ must also be an integer.
+By definition, $\binom{p}{k} = \frac{p!}{k!(p-k)!} = p\frac{(p-1)!}{k!(p-k)!}$.
+Because $p$ and $\frac{(p-1)!}{k!(p-k)!}$ are both integers, this implies that $p \vert \binom{p}{k}$.
 
@@
 \]
-Since $p \vert \binom{p}{k}$ for all $k < p$ and all numbers between 1 and $p$-1
-(inclusive) as less than $p$, $\sum_{k=0}^{p} \binom{p}{k} a^{p-k}b^k$ is divisible
-by $p$.  This means that $\sum_{k=0}^{p} \binom{p}{k} a^{p-k}b^k \equiv 0$ (mod p).
+Since $p \vert \binom{p}{k}$ for all $k < p$ and all numbers between 1 and $p-1$
+(inclusive) are less than $p$, $\sum_{k=1}^{p-1} \binom{p}{k} a^{p-k}b^k$ is divisible
+by $p$.  This means that $\sum_{k=1}^{p-1} \binom{p}{k} a^{p-k}b^k \equiv 0$ (mod $p$).
 Consequently,
@@
 and let $a^{-1}$ be its inverse.  Also assume $a$ is a zero divisor and let
-$ab \equiv 0$ (mod $m$) for some nonzero element $b$ of $\mathbb{Z}/m\mathbb{Z}$
-(by definition of zero divisor).
+$ab \equiv 0$ (mod $m$) for some nonzero element $b$ of $\mathbb{Z}/m\mathbb{Z}$.
 As such,
@@
 \]
-Thus, $b \equiv 0$ (mod $m$).  This is a contradiction.  Therefore, $a$ cannot
+Therefore, $b \equiv 0$ (mod $m$).  This is a contradiction.  Therefore, $a$ cannot
 be a zero divisor and a unit.
@@
 and is a zero element of $\mathbb{Z}/m\mathbb{Z}$.
-Let $x = {p_0}^{x_0} ... {p_k}^{x_k}$ such that $x_i \cdot a_i = max(a_i, m_i)$
-for all $i$.  Thus, $ax \equiv d \equiv 0$ (mod m).  We know that $x$ is a nonzero
-element because $x$ could only be a nonzero element if $x_i = 0$ for all $i$,
-implying that $max(a_i, m_i) = 0$ for all $i$ (which would only be true if $a = 1$ and
-$p = 1$).  Therefore, if $(a, m) \neq 1$, then $a$ is a zero divisor.
+Let $x = {p_0}^{x_0} ... {p_k}^{x_k}$ such that ${x_i}{a_i} = max(a_i, m_i)$
+for all $i$.  That is, $ax \equiv d \equiv 0$ (mod m).
+Therefore, if $(a, m) \neq 1$, then $a$ is a zero divisor.
+
+\item Let $ua = 1$ and $ub = 1$ for elements $a, b$ in $\mathbb{Z}/m\mathbb{Z}$.
+As such,
+\[
+uab = (ua)b = 1b = b
+\]
+and
+\[
+uab = (ub)a = 1a = a.
+\]
+Therefore, $a = b$, proving that $u$ has exactly one inverse.
 

### 2019-09-16 hw1/MSimonsHW1.tex
hw1 revisions

--- 2019-09-05 MSimonsHW1.tex
@@
 
-\item \textbf{a} We can prove the statement by induction.
-First, let $n = 1$.
-As such, $n^2 = 1$.
-By the Division Algorithm, $n^2 = 8*0 + 1$.
-Thus, the statement holds for $n = 1$.
-Next, assume the statement holds for $1, 3, 5, ..., n$.
-Since $n$ is odd, the next consecutive odd number is $n+2$.
-Because $n^2$ leaves a remainder of 1 when divided by 8, let $n^2 = 8*k + 1$ for some integer $k$.
-As such, $(n+2)^2 = n^2 + 4*n + 4 = 64*k^2 + 48*k + 9 = 8 * (8*k^2 + 6*k + 1) + 1$.
-Therefore, $(n+2)^2$ leaves a remainder of 1 when divided by 8.
-By induction, for any odd number $n$, $n$ leaves a remainder of 1 when divided by 8.
+\item \textbf{a} We can prove the statement by induction.  First, let $n = 1$.
+As such, $n^2 = 1$.  By the Division Algorithm, $n^2 = 8\cdot 0 + 1$.  Thus, the
+statement holds for $n = 1$.  Next, assume the statement holds for $1, 3, 5, ..., n$.
+  Since $n$ is odd, the next consecutive odd number is $n+2$.  Because $n^2$
+  leaves a remainder of 1 when divided by 8, let $n^2 = 8\cdot k + 1$ for some integer $k$.
+  As such, $(n+2)^2 = n^2 + 4\cdot n + 4 = 8k + 4n + 1$.
+  Therefore, $(n+2)^2$ leaves a remainder of 1 when divided by 8.  By induction,
+  for any odd number $n$, $n$ leaves a remainder of 1 when divided by 8.
 
-\textbf{b} Let $n = 2^{a_0} * {p_1}^{a_1} * {p_2}^{a_2} * ...
-* {p_k}^{a_k}$ be the prime factorization of $n$ such that $p_i$ are distinct prime numbers for all $i$ and there is no $i$ such that $p_i = 2$.
-As such, $n^2 = 2^{2a_0} * {p_1}^{2a_1} * {p_2}^{2a_2} * ...
-* {p_k}^{2a_k}$.
-Since $p_i$ is odd for all $i$ (since all $p_i$ are primes and do not equal 2), ${p_1}^{a_1} * {p_2}^{a_2} * ...
-* {p_k}^{a_k}$ is also odd.
-By $1a$, ${p_1}^{2a_1} * {p_2}^{2a_2} * ...
-* {p_k}^{2a_k}$ leaves a remainder of 1 when divided by 8.
-Let ${p_1}^{2a_1} * {p_2}^{2a_2} * ...
-* {p_k}^{2a_k} = 8b + 1$ for some integer $b$.
-Thus, $n^2 = 2^{2a_0} * (8b + 1) = 4^{a_0} * (8b + 1) = 8 * (4^{a_0}b) + 4^{a_0}.$  Since factors of 4 can only leave a remainder of either 0 or 4 when divided by 8 and $n^2 = 8 * (4^{a_0}b) + 4^{a_0}$, $n^2$ can only leave a remainder or 0 or 4 when divided by 8.
+\textbf{b} Let $n = 2^{a_0} \cdot  {p_1}^{a_1} \cdot  {p_2}^{a_2} \cdot  ... \cdot  {p_k}^{a_k}$
+be the prime factorization of $n$ such that $p_i$ are distinct prime numbers for
+all $i$ and there is no $i$ such that $p_i = 2$.
+As such, $n^2 = 2^{2a_0} \cdot  {p_1}^{2a_1} \cdot  {p_2}^{2a_2} \cdot  ... \cdot  {p_k}^{2a_k}$.
+Since $p_i$ is odd for all $i$ (since all $p_i$ are primes and do not equal 2),
+${p_1}^{a_1} \cdot  {p_2}^{a_2} \cdot  ... \cdot  {p_k}^{a_k}$ is also odd.
+By $1a$, ${p_1}^{2a_1} \cdot  {p_2}^{2a_2} \cdot  ... \cdot  {p_k}^{2a_k}$ leaves
+a remainder of 1 when divided by 8.  Let ${p_1}^{2a_1} \cdot  {p_2}^{2a_2} \cdot  ... \cdot  {p_k}^{2a_k} = 8b + 1$
+for some integer $b$.  Thus, $n^2 = 2^{2a_0} \cdot  (8b + 1) = 4^{a_0} \cdot  (8b + 1) = 8 \cdot  (4^{a_0}b) + 4^{a_0}.$
+Since multiples of 4 can only leave a remainder of either 0 or 4 when divided by 8
+($4(2k) = 8k$ and $4(2k + 1) = 8k + 4$ for all integers $k$)
+and $n^2 = 8 \cdot  (4^{a_0}b) + 4^{a_0}$, $n^2$ can only leave a remainder or 0 or 4
+when divided by 8.
 
@@
 First, assume $n = 3k + 1$.
-Thus, $n^2 - 1 = (3k + 1)^2 - 1 = 3 * (3k^2 + 2k)$.
+Thus, $n^2 - 1 = (3k + 1)^2 - 1 = 3 \cdot  (3k^2 + 2k)$.
 Therefore, $3 \vert (n - 1)^2$ for this case.
 Next, assume $n = 3k + 2$.
-Thus, $n^2 - 1 = (3k + 2)^2 - 1 = 3 * (3k^2 + 4k + 1)$.
+Thus, $n^2 - 1 = (3k + 2)^2 - 1 = 3 \cdot  (3k^2 + 4k + 1)$.
 Therefore, $3 \vert (n - 1)^2$ for all $n$ such that $3 \nmid n$.
 
-\item Let $a = {p_1}^{x_1} * ...
-* {p_k}^{x_k}$ and $b = {p_1}^{y_1} * ...
-* {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.
-Let $c = {q_1}^{z_1} * ...
-* {q_j}^{z_j}$ be the prime factorization of $c$ given there are no $m, n$ such that $p_m = q_n$.
+\item Let $a = {p_1}^{x_1} \cdot  ...
+\cdot  {p_k}^{x_k}$ and $b = {p_1}^{y_1} \cdot  ...
+\cdot  {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.
+Let $c = {q_1}^{z_1} \cdot  ...
+\cdot  {q_j}^{z_j}$ be the prime factorization of $c$ given there are no $m, n$ such that $p_m = q_n$.
 This holds because $(a, c) = 1$ and $(b, c) = 1$, meaning $a$ and $c$ have no common prime factors and $b$ and $c$ have no common prime factors.
-Thus, $ab = {p_1}^{x_1 + y_1} * ...
-* {p_k}^{x_k + y_k}$.
+Thus, $ab = {p_1}^{x_1 + y_1} \cdot  ...
+\cdot  {p_k}^{x_k + y_k}$.
 Therefore, $ab$ and $c$ also do not have any common prime factors.
@@
 Next suppose $(a, b) \neq 1$.
-Let $a = {p_1}^{x_1} * ...
-* {p_k}^{x_k}$ and $b = {p_1}^{y_1} * ...
-* {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.
-If $a$ and $b$ both divide $c$, then $m = {p_1}^{max(x_1, y_1)} * ...
-* {p_k}^{max(x_k, y_k)}$ is a factor of $c$.
-If $(a,b) = {p_1}^{min(x_1, y_1)} * ...
-* {p_k}^{min(x_k, y_k)}$, then  $m * (a,b) = ab$.
-Let $c = m*x$ for some integer $x$.
-Thus, $c = m*x*(a,b) = a*b*x$ is divisible by $ab$.
+Let $a = {p_1}^{x_1} \cdot  ...
+\cdot  {p_k}^{x_k}$ and $b = {p_1}^{y_1} \cdot  ...
+\cdot  {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.
+If $a$ and $b$ both divide $c$, then $m = {p_1}^{max(x_1, y_1)} \cdot  ...
+\cdot  {p_k}^{max(x_k, y_k)}$ is a factor of $c$.
+If $(a,b) = {p_1}^{min(x_1, y_1)} \cdot  ...
+\cdot  {p_k}^{min(x_k, y_k)}$, then  $m \cdot  (a,b) = ab$.
+Let $c = m\cdot x$ for some integer $x$.
+Thus, $c = m\cdot x\cdot (a,b) = a\cdot b\cdot x$ is divisible by $ab$.
 
-\item If $(a, 6) = 1$, then either $a = 6x + 1$ or $a = 6x - 1$ for some integer $x$.
+\item If $(a, 6) = 1$, then either $a = 6x + 1$ or $a = 6x - 1$ for some integer $x$
+(since $(k, 6) > 1$ for all $2 \leq k \leq 4$).
 Similarly, either $b = 6y + 1$ or $b = 6y - 1$.
@@
 By the same logic, $b^2$ also always leaves a remainder of 1 when divided by 24.
-Let $a^2 = 24m + 1$ and $b^2 = 24n + 1$ for some integers $m, n < 24$.
+Let $a^2 = 24m + 1$ and $b^2 = 24n + 1$ for some integers $m, n$.
 Therefore, $a^2 - b^2 = (24m + 1) - (24n + 1) = 24(m-n)$, which is divisible by 24.
@@
 \item First, assume $n$ is a square number.
-If $n = {p_1}^{a_1} * ...
-* {p_k}^{a_k}$, then $\sqrt n = {p_1}^{a_1/2} * ...
-* {p_k}^{a_k/2}$.
+If $n = {p_1}^{a_1} \cdot  ...
+\cdot  {p_k}^{a_k}$, then $\sqrt n = {p_1}^{a_1/2} \cdot  ...
+\cdot  {p_k}^{a_k/2}$.
 By the definition of prime factorization, $a_i$ and $a_i/2$ must be integers for all $i$ such that $1 \leq i \leq k$.
@@
 Let $a_i = 2b_i$ for some integers $b_i$.
-Thus, $n = {p_1}^{2b_1} * ...
-* {p_k}^{2b_k}$.
-Since each $b_i$ is an integer, $\sqrt n = {p_1}^{b_1} * ...
-* {p_k}^{b_k}$ is an integer and $n$ must be a square number.
+Thus, $n = {p_1}^{2b_1} \cdot  ...
+\cdot  {p_k}^{2b_k}$.
+Since each $b_i$ is an integer, $\sqrt n = {p_1}^{b_1} \cdot  ...
+\cdot  {p_k}^{b_k}$ is an integer and $n$ must be a square number.
 
-\item Let $a = {p_1}^{x_1} * ...
-* {p_k}^{x_k}$ and $b = {q_1}^{y_1} * ...
-* {q_j}^{y_j}$ be the prime factorizations of $a$ and $b$ respectively such that $p_m \neq q_n$ for all $m, n$.
-As such, $ab = {p_1}^{x_1} * ...
-* {p_k}^{x_k} * {q_1}^{y_1} * ...
-* {q_j}^{y_j}$.
+\item Let $a = {p_1}^{x_1} \cdot  ...
+\cdot  {p_k}^{x_k}$ and $b = {q_1}^{y_1} \cdot  ...
+\cdot  {q_j}^{y_j}$ be the prime factorizations of $a$ and $b$ respectively such that $p_m \neq q_n$ for all $m, n$.
+As such, $ab = {p_1}^{x_1} \cdot  ...
+\cdot  {p_k}^{x_k} \cdot  {q_1}^{y_1} \cdot  ...
+\cdot  {q_j}^{y_j}$.
 If $ab$ is a square, then $x_1, ..., x_k$ and $y_1, ..., y_j$ must be even.

### 2019-09-17 hw3/MSimonsHW3.tex
Starting hw3 problem 5

\documentclass{article}
\title{Homework 3}
\author{Madilyn Simons}
\date{}
\setlength{\parindent}{0pt}
\pdfpagewidth 8.5in
\pdfpageheight 11in

\usepackage{amssymb}
\usepackage{amsmath}

\begin{document}
\maketitle

\begin{enumerate}

\item TODO

\item TODO

\item TODO

\item TODO

\item Assume $M$ is a unit.  Therefore there exists some $M^{-1} \in M_2(\mathbb{Z})$
such that $MM^{-1} = I_2$.  We find $M^{-1}$ using Gaussian Elimination:
\[
\left[
\begin{array}{cc|cc}
a & b & 1 & 0 \\
c & d & 0 & 1
\end{array}
\right]
\Leftrightarrow
\left[
\begin{array}{cc|cc}
a & b & 1 & 0 \\
0 & \frac{ad-bc}{a} & \frac{-c}{a} & 1
\end{array}
\right]
\]
\[
\Leftrightarrow
\left[
\begin{array}{cc|cc}
a & b & 1 & 0 \\
0 & 1 & \frac{-c}{ad-bc} & \frac{a}{ad-bc}
\end{array}
\right]
\Leftrightarrow
\left[
\begin{array}{cc|cc}
a & 0 & \frac{ad}{ad-bc} & \frac{-ab}{ad-bc} \\
0 & 1 & \frac{-c}{ad-bc} & \frac{a}{ad-bc}
\end{array}
\right]
\]
\[
\Leftrightarrow
\left[
\begin{array}{cc|cc}
1 & 0 & \frac{d}{ad-bc} & \frac{-b}{ad-bc} \\
0 & 1 & \frac{-c}{ad-bc} & \frac{a}{ad-bc}
\end{array}
\right]
\]

Therefore $M^{-1} = \begin{bmatrix} \frac{d}{ad-bc} & \frac{-b}{ad-bc} \\
\frac{-c}{ad-bc} & \frac{a}{ad-bc}\end{bmatrix}$.  Since $M^{-1} \in M_2(\mathbb{Z})$,
each of its elements must be integers.  Its elements can only be
integers if $ad-bc$ evenly divides $a$, $b$, $c$, and $d$. \\
\\
First, assume $a$, $b$, $c$, and $d$ are relatively prime.  If so, then the
only integers that evenly divide all four are $\pm1$.  Therefore
${ad-bc}$ must be $\pm1$. \\
\\
Otherwise, $a$, $b$, $c$, and $d$ are not relatively prime.  Let $m$ be the
greatest common factor of the $a$, $b$, $c$, and $d$.  Now, let $a = mx$,
$b = my$, $c = mz$ and $d = mw$ for some integers $x$, $y$, $z$, and $w$.
As such, $ad - bc = m^2xw - m^yz = m^2(xw - yz)$.  This means that
$m^2$ and $(xw - yz)$ must also be common factors of $a$, $b$, $c$, and $d$.
If $m$ is the greatest common factor, then $m^2 \leq \vertm\vert$.  This is only
possible if $m = 1$.  Likewise, $\vert(xw - yz)\vert \leq \vertm\vert$.
Since $m = 1$, $(xw - yz)$ must be $\pm1$ or $0$, but it can't be $0$ since
$m^2 \cdot 0 = 0$, which can't divide any integer.  Since $m^2 = 1$ and
$xw - yz = \pm1$, $ad - bc = \pm1$.

\end{enumerate}
\end{document}

### 2019-09-19 hw3/MSimonsHW3.tex
First half of prob 5 for hw 3
Finished number 5 in hw 3

@@
 \\
-First, assume $a$, $b$, $c$, and $d$ are relatively prime.  If so, then the
-only integers that evenly divide all four are $\pm1$.  Therefore
-${ad-bc}$ must be $\pm1$. \\
+Let $m$ be the greatest common denominator of $a$, $b$, $c$, and $d$.
+Let $a = mx$, $b = my$, $c = mz$, and $d = mw$ for some integers
+$x$, $y$, $z$, and $w$ that are not divisible by $m$.
+As such $ad-bc = mxmw - mymz = m^2(xw - yz)$.  Since $m$ is the greatest common
+denominator and $m^2$ is also a common denominator, $m^2 \leq m$ and this is
+only possible if $m = 1$.  Therefore, the greatest common denominator of
+$a$, $b$, $c$, and $d$ is 1.  If this is the case, $ad-bc$ must be $\pm1$ since
+only $\pm1$ can evenly $a$, $b$, $c$, and $d$.
 \\
-Otherwise, $a$, $b$, $c$, and $d$ are not relatively prime.  Let $m$ be the
-greatest common factor of the $a$, $b$, $c$, and $d$.  Now, let $a = mx$,
-$b = my$, $c = mz$ and $d = mw$ for some integers $x$, $y$, $z$, and $w$.
-As such, $ad - bc = m^2xw - m^yz = m^2(xw - yz)$.  This means that
-$m^2$ and $(xw - yz)$ must also be common factors of $a$, $b$, $c$, and $d$.
-If $m$ is the greatest common factor, then $m^2 \leq \vertm\vert$.  This is only
-possible if $m = 1$.  Likewise, $\vert(xw - yz)\vert \leq \vertm\vert$.
-Since $m = 1$, $(xw - yz)$ must be $\pm1$ or $0$, but it can't be $0$ since
-$m^2 \cdot 0 = 0$, which can't divide any integer.  Since $m^2 = 1$ and
-$xw - yz = \pm1$, $ad - bc = \pm1$.
+\\
+Next, assume $ad - bc = \pm1$.  By the last proof, $M$ can only be a unit if
+$MM^{-1} = I_2$ and $M^{-1} \in M_2(\mathbb{Z})$.  If $ad - bc = 1$, then
+$M^{-1} = \begin{bmatrix} d & -b \\ -c & a \end{bmatrix}$ and $MM^{-1} = I_2$.
+If $ad - bc = -1$, then $M^{-1} = \begin{bmatrix} -d & b \\ c & -a \end{bmatrix}$
+and $MM^{-1} = I_2$.
+\\
+\\
+Thus, $M \in M_2(\mathbb{Z})$ is a unit if and only if $ad - bc = \pm1$.
 

### 2019-09-19 hw3/MSimonsHW3.tex
problem 2 hw 3

@@
 
-\item TODO
+\item The set $\frac{1}{2}\mathbb{Z}$ is not a ring.  A ring must be closed under
+multiplication.  Let $a = \frac{m}{2}$ and $b = \frac{n}{2}$ for some integers
+$m$, $n$.  We know that $ab = \frac{mn}/4$.  Assume $m$ and $n$ are both odd and
+that $m = 2x + 1$ and $n = 2y + 1$ for some integers $x$, $y$.  Therefore,
+\[
+ab = \frac{mn}{4} = \frac{(2x+1)(2y+1)}{4} = \frac{2(2xy+y)+1}{4}
+\]
+Since $ab$ is not an element of the set, this means that the set is not closed
+under multiplication.
 
-\item TODO
+\item This set is a ring. \\
+Let $a = \frac{m}{2x+1}$, $b=\frac{n}{2y+1}$, $c=\frac{l}{2z+1}$ be elements of
+the set for some integers $m$, $n$, $l$, $x$, $y$, and $z$.\\
+The set is closed under addition:
+\[
+a + b = \frac{m}{2x+1} + frac{n}{2y+1} = \frac{m(2y+1) + 2(nx+1)}{2(2xy+x+y)+1}
+\]
+Associative addition holds:
+\[
+a+(b+c) = \frac{m}{2x+1} + (\frac{n}{2y+1} + \frac{l}{2z+1})
+\]
+\[
+= \frac{m(2y+1)(2z+1) + n(2z+1)(2x+1) + l(2y+1)(2x+1)}{(2x+1)(2y+1)(2z+1)}
+\]
+\[
+= (\frac{m}{2x+1} + \frac{n}{2y+1}) + \frac{l}{2z+1} = (a+b)+c
+\]
+Commutative addition holds:
+\[
+a + b = \frac{m}{2x+1} + \frac{n}{2y+1}
+\]
+\[
+= \frac{m(2y+1) + 2(nx+1)}{2(2xy+x+y)+1}
+\]
+\[
+= \frac{n}{2y+1} + \frac{m}{2x+1} = b + a
+\]
+There exists an $0$ element in the set such that:
+\[
+a + 0 = \frac{m}{2x+1} + \frac{0}{1} = \frac{m}{2x+1} = a
+= \frac{0}{1} + \frac{m}{2x+1} = 0 + a
+\]
+There is a solution to $a + x = 0$.  Let $x = \frac{-m}{2x+1}$:
+\[
+a + x = \frac{m}{2x+1} + \frac{-m}{2x+1} = \frac{m + {-m}}{2x+1} = \frac{0}{2x+1} = 0
+\]
+The set is closed under multiplication:
+\[
+ab = \frac{m}{2x+1}\cdot\frac{n}{2y+1} = \frac{mn}{(2x+1)(2y+1)} = \frac{mn}{2(2xy+x+y)+1}
+\]
+Associative multiplication holds:
+\[
+a(bc) = \frac{m}{2x+1}\cdot(\frac{n}{2y+1}\cdot\frac{l}{2z+1}) = (\frac{m}{2x+1}\cdot\frac{n}{2y+1})\cdot\frac{l}{2z+1}
+= (ab)c
+\]
+The Distributive Property holds:
+\[
+a(b+c) = \frac{m}{2x+1}\cdot(\frac{n}{2y+1}+\frac{l}{2z+1})
+= \frac{m}{2x+1}\cdot(\frac{n(2z+1) + l(2y+1)}{(2y+1)(2z+1)})
+\]
+\[
+= \frac{m}{2x+1}\cdot\frac{n}{2y+1} + \frac{m}{2x+1}\cdot\frac{l}{2z+1}
+=ab+ac
+\]
 

### 2019-09-22 hw2/MSimonsHW2.tex
Revisions to hw2

@@
 
-\item Since $k < p$ and $(p-k) < p$, neither $k!$ nor $(p-k)!$ have any prime factors that divide $p$.
+\item Since $k < p$ and $(p-k) < p$, neither $k!$ nor $(p-k)!$ have any prime
+factors that divide $p$, implying $gcd(p, k!(p-k)!) = 1$.
 Because of this and the fact that $\frac{p!}{k!(p-k)!}$ is an integer,
@@
 By definition, $\binom{p}{k} = \frac{p!}{k!(p-k)!} = p\frac{(p-1)!}{k!(p-k)!}$.
-Because $p$ and $\frac{(p-1)!}{k!(p-k)!}$ are both integers, this implies that $p \vert \binom{p}{k}$.
+Because $p$ and $\frac{(p-1)!}{k!(p-k)!}$ are both integers, this implies that
+$p \vert \binom{p}{k}$.
 
@@
 \]
-Since $p \vert \binom{p}{k}$ for all $k < p$ and all numbers between 1 and $p-1$
-(inclusive) are less than $p$, $\sum_{k=1}^{p-1} \binom{p}{k} a^{p-k}b^k$ is divisible
+Since $p \vert \binom{p}{k}$ for all $k < p$,
+$\sum_{k=1}^{p-1} \binom{p}{k} a^{p-k}b^k$ is divisible
 by $p$.  This means that $\sum_{k=1}^{p-1} \binom{p}{k} a^{p-k}b^k \equiv 0$ (mod $p$).
@@
 \item Let $a$ be some element of $\mathbb{Z}/m\mathbb{Z}$.  Assume $a$ is a unit
-and let $a^{-1}$ be its inverse.  Also assume $a$ is a zero divisor and let
+and let $a^{-1}$ be its inverse.  Also assume $a$ is a zero divisor, so
 $ab \equiv 0$ (mod $m$) for some nonzero element $b$ of $\mathbb{Z}/m\mathbb{Z}$.
@@
 some $d = {p_0}^{max(a_0, m_0)} ... {p_k}^{max(a_k, m_k)}$, which is divisible by $a$
-and is a zero element of $\mathbb{Z}/m\mathbb{Z}$.
-Let $x = {p_0}^{x_0} ... {p_k}^{x_k}$ such that ${x_i}{a_i} = max(a_i, m_i)$
+and is a zero element of $\mathbb{Z}/m\mathbb{Z}$ because it is a multiple of $m$.
+Let $x = {p_0}^{x_0} ... {p_k}^{x_k}$ such that ${x_i}+{a_i} = max(a_i, m_i)$
 for all $i$.  That is, $ax \equiv d \equiv 0$ (mod m).
-Therefore, if $(a, m) \neq 1$, then $a$ is a zero divisor.
+Therefore, if $(a, m) \neq 1$, then $a$ is a zero divisor because $x \not\equiv 0$ (mod $m$).
 

### 2019-09-26 hw4/MSimonsHW4.tex
Starting hw4

--- 2019-09-17 hw3/MSimonsHW3.tex
@@
 \documentclass{article}
-\title{Homework 3}
+\title{Homework 4}
 \author{Madilyn Simons}
@@
 
-\item Assume $M$ is a unit.  Therefore there exists some $M^{-1} \in M_2(\mathbb{Z})$
-such that $MM^{-1} = I_2$.  We find $M^{-1}$ using Gaussian Elimination:
-\[
-\left[
-\begin{array}{cc|cc}
-a & b & 1 & 0 \\
-c & d & 0 & 1
-\end{array}
-\right]
-\Leftrightarrow
-\left[
-\begin{array}{cc|cc}
-a & b & 1 & 0 \\
-0 & \frac{ad-bc}{a} & \frac{-c}{a} & 1
-\end{array}
-\right]
-\]
-\[
-\Leftrightarrow
-\left[
-\begin{array}{cc|cc}
-a & b & 1 & 0 \\
-0 & 1 & \frac{-c}{ad-bc} & \frac{a}{ad-bc}
-\end{array}
-\right]
-\Leftrightarrow
-\left[
-\begin{array}{cc|cc}
-a & 0 & \frac{ad}{ad-bc} & \frac{-ab}{ad-bc} \\
-0 & 1 & \frac{-c}{ad-bc} & \frac{a}{ad-bc}
-\end{array}
-\right]
-\]
-\[
-\Leftrightarrow
-\left[
-\begin{array}{cc|cc}
-1 & 0 & \frac{d}{ad-bc} & \frac{-b}{ad-bc} \\
-0 & 1 & \frac{-c}{ad-bc} & \frac{a}{ad-bc}
-\end{array}
-\right]
-\]
+\item TODO
 
-Therefore $M^{-1} = \begin{bmatrix} \frac{d}{ad-bc} & \frac{-b}{ad-bc} \\
-\frac{-c}{ad-bc} & \frac{a}{ad-bc}\end{bmatrix}$.  Since $M^{-1} \in M_2(\mathbb{Z})$,
-each of its elements must be integers.  Its elements can only be
-integers if $ad-bc$ evenly divides $a$, $b$, $c$, and $d$. \\
-\\
-First, assume $a$, $b$, $c$, and $d$ are relatively prime.  If so, then the
-only integers that evenly divide all four are $\pm1$.  Therefore
-${ad-bc}$ must be $\pm1$. \\
-\\
-Otherwise, $a$, $b$, $c$, and $d$ are not relatively prime.  Let $m$ be the
-greatest common factor of the $a$, $b$, $c$, and $d$.  Now, let $a = mx$,
-$b = my$, $c = mz$ and $d = mw$ for some integers $x$, $y$, $z$, and $w$.
-As such, $ad - bc = m^2xw - m^yz = m^2(xw - yz)$.  This means that
-$m^2$ and $(xw - yz)$ must also be common factors of $a$, $b$, $c$, and $d$.
-If $m$ is the greatest common factor, then $m^2 \leq \vertm\vert$.  This is only
-possible if $m = 1$.  Likewise, $\vert(xw - yz)\vert \leq \vertm\vert$.
-Since $m = 1$, $(xw - yz)$ must be $\pm1$ or $0$, but it can't be $0$ since
-$m^2 \cdot 0 = 0$, which can't divide any integer.  Since $m^2 = 1$ and
-$xw - yz = \pm1$, $ad - bc = \pm1$.
+\item TODO
 

### 2019-09-26 hw4/MSimonsHW4.tex
Problems 2, 5, and 6 for hw4

@@
 
-\item TODO
+\item Consider ${\mathbb{Z}}_4 = {0, 1, 2, 3}$.  We know 0 is not a zero divisor since
+a zero divisor is a nonzero element by definition.  We know that 1 is not a zero
+because $1x = x$ for all $x$  and then $x$ must be 0 if $1x = 0$.  We know that
+2 IS a zero divisor because $2\cdot2 = 4 = 0$.  We know that 3 is not a zero
+divisor because 3 and 4 are relatively prime, meaning any zero element of
+${\mathbb{Z}}_4$ must be a multiple of 4, which equals 0.  Therefore, there
+does exist a ring with one zero divisor.
+
+\item First, let us prove that $\cong$ is symmetric.
+Since $f: R \rightarrow S$ is an isomorphism, this means that $f$ is bijective.
+Let $f(r) = s$ for some $r \in R$ and some $s \in S$.
+If $f$ is bijective, there exists some function $g: S \rightarrow R$ such that
+$g(s) = g(f(r)) = r$. \\ \\
+To prove $g$ is injective, let $s, s' \in S$ and $r, r' \in R$ such that
+$s \neq s'$, $r \neq r'$, $f(s) = r$, and $f(s') = r'$.  As such,
+$g(s) = g(f(r)) = r$ and $g(s') = g(f(r')) = r'$.  Since $r \neq r'$, this
+implies that if $s \neq s'$, then $r \neq r'$ and $g$ must be injective. \\ \\
+Because Im $f$ = $S$, there is an $r \in R$ for all $s \in S$ such that
+$s = f(r)$.  Because $g(s) = g(f(r)) = r$, Im $g$ = $R$ and $g$ is surjective. \\ \\
+We can prove that $g(s) + g(s') = g(s + s')$ as such: \\
+\[
+g(s) + g(s') = g(f(r)) + g(f(r')) = r + r' = g(f(r + r')) = g(f(r) + f(r')) = g(s + s')
+\]
+\\
+We can prove $g(s)g(s') = g(ss')$ as such:
+\[
+g(s)g(s') = g(f(r))g(f(r')) = rr' = g(f(rr')) = g(f(r)f(r')) = g(ss')
+\]
+\\
+Therefore, $g$ is an isomorphism and $\cong$ is symmetric.
+\\ \\
+Next, we prove that $\cong$ is transitive.  If $f$ and $g$ are isomorphisms,
+then there exists $r \in R$, $s \in S$, and $t \ in T$ such that
+$f(r) = s$ and $g(s) = t$.  As such, let $h: R \rightarrow T$ be the function
+such that $h(r) = g(f(r)) = g(s) = t$. \\ \\
+Let $g(s') = t'$ for some $s' \in S$ and $t' in T$ such that
+$s \neq s'$ and $t \neq t'$.
+We know $h$ is injective because $h(r) = g(f(r)) = g(s) = t$ and
+$h(r') = g(f(r')) = g(s') = t'$ and $t \neq t'$.
+\\ \\
+We know $h$ is surjective because the Im $f$ is $S$ and Im $g$ is $T$.
+Therefore, for all $t \in T$ there is a solution to $h(r) = t$.
+\\ \\
+We prove $h(r) + h(r') = h(r + r')$ as such:
+\[
+h(r) + h(r') = g(f(r)) + g(f(r')) = g(f(r + r')) = h(r + r')
+\]
+\\
+We prove $h(r)h(r') = h(rr')$ as such:
+\[
+h(r)h(r') = g(f(r))g(f(r')) = g(f(r)f(r')) = g(f(rr')) = h(rr')
+\]
+Therefore $h$ is an isomorphism and $\cong$ is transitive.
 
@@
 
-\item TODO
+\item Let $f: R \rightarrow \mathbb{Q}[\sqrt{2}]$ be the function
+$f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix})$ = $a + b\sqrt2$ such that
+$a, b \in \mathbb{Q}$. \\ \\
 
-\item TODO
+To prove injection, let $c, d \in \mathbb{Q}$ such that $a \neq c$ and $b \neq d$.
+Also, assume $f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}) = f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})$.
+As such:
+\[
+f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}) = f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix}) \\
+a + b\sqrt2 = c + d\sqrt2
+a - c = \sqrt{2}(d - b)
+\sqrt2 = (a - c)/(d - b)
+\]
+Since $\sqrt2$ is an irrational number and $(a-c)/(d-b)$ is a rational number,
+this is a contradiction.  Thus, $f$ is injective. \\ \\
+We know that $f$ is surjective because Im $f = \mathbb{Q}$. \\ \\
 
-\item TODO
+We can prove
+$f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}) + f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})
+= f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix} + \begin{bmatrix} c & d \\ 2d & c \end{bmatrix})$
+ as such:
+ \[
+ f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}) + f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})
+ \] \[
+ = (a + bi) + (c+di) = (a+c) + (b+d)i
+ \] \[
+ = f(\begin{bmatrix} a+c & b+d \\ 2(b+d) & a+c \end{bmatrix})
+ \] \[
+ = f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix} + \begin{bmatrix} c & d \\ 2d & c \end{bmatrix})
+ \]
+ \\
+ We can prove
+ $f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix})f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})
+ = f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})$
+ as such:
+ \[
+f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix})f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})
+ \] \[
+= (a+b\sqrt2)(c+d\sqrt2) = (ac + 2bd) + (ad + bc)\sqrt2
+ \] \[
+ = f(\begin{bmatrix} ac+2bd & ad+bc \\ 2(ad+bc) & ac + 2bd\end{bmatrix})
+ = f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})
+ \]
+ \\
+ Therefore, $f$ is an isomorphism and $R$ is isomorphic to $\mathbb{Q}[\sqrt2]$.
+
+\item The rings are not isomorphic because
+$\mathbb{Z}/6\mathbb{Z} \times \mathbb{Z}/35\mathbb{Z}$
+is a 170-element set and
+$\mathbb{Z}/10\mathbb{Z} \times \mathbb{Z}/21\mathbb{Z}$
+is an 180-element set and it is not possible to have a surjective
+function from an 170-element set to an 180-element set.
 

### 2019-09-26 hw4/MSimonsHW4.tex
number 3 hw 4

@@
 such that $h(r) = g(f(r)) = g(s) = t$. \\ \\
-Let $g(s') = t'$ for some $s' \in S$ and $t' in T$ such that
+Let $g(s') = t'$ for some $s' \in S$ and $t' \in T$ such that
 $s \neq s'$ and $t \neq t'$.
@@
 
-\item TODO
+\item Assume $\mathbb{C}$ and $\mathbb{R}$ are isomorphic and
+$f: \mathbb{C} \rightarrow \mathbb{R}$.  By the definition of isomorphism,
+we know that $f(1) = f(1\cdot1) = f(1)f(1) = f(1)^2$.  If $f(1) = f(1)^2$, then
+$f(1)$ must either be 0 or 1.  Assume $f(1) = 0$.  Then, for an $c \in \mathbb{C}$,
+$f(c) = f(c\cdot1) = f(c)f(1) = f(c)\cdot0 = 0$, and this is a contradiction since
+isomorphisms are bijective.  Therefore, $f(1) = 1$.  Again, by the definition
+of isomorphism, $f(-1) = -f(1) = -1$.  Now let $r = f(i)$.  As such,
+$r^2 = f(i)f(i) = f(i^1) = f(-1) = -1$.  However, this is a contradiction
+because there is no $r \in \mathbb{R}$ such $r^2 = -1$.  Therefore
+$\mathbb{C}$ and $\mathbb{R}$ are not isomorphic.
 

### 2019-09-26 MSimonsHW4.tex
Added MSimonsHW4.pdf and MSimonsHW4.tex via upload

--- 2019-09-26 hw4/MSimonsHW4.tex
@@
 Next, we prove that $\cong$ is transitive.  If $f$ and $g$ are isomorphisms,
-then there exists $r \in R$, $s \in S$, and $t \ in T$ such that
+then there exists $r \in R$, $s \in S$, and $t \in T$ such that
 $f(r) = s$ and $g(s) = t$.  As such, let $h: R \rightarrow T$ be the function
@@
 of isomorphism, $f(-1) = -f(1) = -1$.  Now let $r = f(i)$.  As such,
-$r^2 = f(i)f(i) = f(i^1) = f(-1) = -1$.  However, this is a contradiction
+$r^2 = f(i)f(i) = f(i^2) = f(-1) = -1$.  However, this is a contradiction
 because there is no $r \in \mathbb{R}$ such $r^2 = -1$.  Therefore
@@
 
-\item TODO
+\item Let $F$ denote a function $F: T_{[0,1]} \rightarrow T_{[0,2]}$ such that
+$F(f)(x) = f(\frac{1}{2}x)$ for some $f \in T_{[0,1]}$.  If
+$f_1, f_2 \in T_{[0,1]}$, we can prove $F(f_1 + f_2) = F(f_1) + F(f_2)$ as such:
+\[
+F(f_1+f_2)(x) = (f_1+f_2)(\frac{1}{2}x) = f_1(\frac{1}{2}x)+f_2(\frac{1}{2}x) = F(f_1)(x) + F(f_2)(x)
+\]
+We can prove $F(f_1 f_2) = F(f_1)F(f_2)$ as such:
+\[
+F(f_1 f_2)(x) = (f_1 f_2)(\frac{1}{2}x) = f_1(\frac{1}{2}x) f_2(\frac{1}{2})x = F(f_1)(x)F(f_2)(x)
+\]
+To prove injectivity, assume $F(f_1) = F(f_2)$:
+\[
+F(f_1)(x) = F(f_2)(x)
+\] \[
+f_1(\frac{1}{2}x) = f_2(\frac{1}{2}x)
+\] \[
+f_1(x) = f_2(x)
+\]
+Therefore $F(f_1) = F(f_2)$ implies $f_1 = f_2$. \\ \\
+To prove surjectivity, let $h \in T_{[0,2]}$ and $f(x) = h(2x)$.
+Therefore $F(f)(x) = f(\frac{1}{2}x) = h(x)$, implying that 
+Im $F = T_{[0,2]}$ and $F$ is surjective. \\ \\
+Thus, $T_{[0,1]}$ and $T_{[0,2]}$ are isomorphic.
 
@@
 
-To prove injection, let $c, d \in \mathbb{Q}$ such that $a \neq c$ and $b \neq d$.
+To prove injectivity, let $c, d \in \mathbb{Q}$ such that $a \neq c$ and $b \neq d$.
 Also, assume $f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}) = f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})$.
@@
 \[
-f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}) = f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix}) \\
+f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}) = f(\begin{bmatrix} c & d \\ 2d & c \end{bmatrix})
+\] \[
 a + b\sqrt2 = c + d\sqrt2
+\] \[
 a - c = \sqrt{2}(d - b)
+\] \[
 \sqrt2 = (a - c)/(d - b)
@@
 this is a contradiction.  Thus, $f$ is injective. \\ \\
-We know that $f$ is surjective because Im $f = \mathbb{Q}$. \\ \\
+We know that $f$ is surjective because for all $a+b\sqrt2 \in \mathbb{Q}[\sqrt2]$,
+there is an $\begin{bmatrix} a & b \\ 2b & a \end{bmatrix} \in M_2(\mathbb{R})$ such that
+$f(\begin{bmatrix} a & b \\ 2b & a \end{bmatrix}) = a+b\sqrt2$. \\ \\
 

### 2019-10-01 hw5/MSimonsHW5.tex
HW5 question 1

\documentclass{article}
\title{Homework 5}
\author{Madilyn Simons}
\date{}
\setlength{\parindent}{0pt}
\pdfpagewidth 8.5in
\pdfpageheight 11in

\usepackage{amssymb}
\usepackage{amsmath}

\begin{document}
\maketitle

\begin{enumerate}

\item To prove $\varphi_{\alpha}$ is closed under addition, first let $f$, $g$
be any elements of $S[x]$.  We know that $f+g$ is also an element of
$S[x]$ because the coefficients of $f$ and $g$ are elements of $S$, which is a
ring.  This implies that the coefficients of $f$ and $g$ are closed under
addition, so the coefficients of $f+g$ are also in $S$.
\\ \\
With this having be said, we can prove $\varphi_{\alpha}$ is closed under addition
as such:
\[
\varphi_{\alpha}(f+g) = (f+g)(\alpha) = f(\alpha) + g(\alpha)
= \varphi_{\alpha}(f) + \varphi_{\alpha}(g)
\]
We know $f \cdot g$ is an element of $S[x]$ since $S$ is closed under multiplication,
so the coefficients of $f \cdot g$ are elements of $S$.
\\ \\
We can prove $\varphi_{\alpha}$ is closed under multiplication as such:
\[
\varphi_{\alpha}(f \cdot g) = (f \cdot g)(\alpha) = f(\alpha) \cdot g(\alpha)
= \varphi_{\alpha}(f) \cdot \varphi_{\alpha}(g)
\]
Thus, $\varphi_{\alpha}$ is a ring homomorphism.

\item TODO
\item TODO

\end{enumerate}
\end{document}

### 2019-10-01 hw5/MSimonsHW5.tex
HW 5 number 2

@@
 
-\item TODO
+\item Let $f(\alpha)$, $g(\alpha)$ be any elements in $S[\alpha]$.  By the
+definition of $S[\alpha]$, $f(x)$, $g(x)$ as elements of $S[x]$.  Since $S[x]$
+is a ring homomorphism, $(f+g)(x)$ is an element of $S[x]$.  If $(f+g)(x)$ is an
+element of $S[x]$, then $(f+g)(\alpha)$ is an element of $S[\alpha]$ and
+$S[\alpha]$ is closed under addition.
+\\
+\\
+Similarly, $f(x)g(x)$ is an element of $S[x]$.  This implies that
+$f(\alpha)g(\alpha)$ is an element of $S[\alpha]$ and so $S[\alpha]$ is
+closed under multiplication.
+\\
+\\
+For $S[\alpha]$ to be a subring of $R$, $0_R$ must be an element of $S[\alpha]$.
+Define the function $f:S[x] \rightarrow R$ by $f(x) = 0_R$.  As such,
+$f(\alpha) = 0_R$ is an element of $S[\alpha]$.
+\\
+\\
+Let $f(x) = a_0 + a_{1}x + ... + a_{n}x^n$ be any element of $S[x]$.
+By definition, $a_i$ is an element of $R$ for all non-negative integers $i$, and
+for all $a_i$, there exists a $b_i$ in $R$ such that $a_i + b_i = 0_R$.
+Therefore, there exists a function $g(x) = b_0 + b_{1}x + ... + b_{n}x^n$ in
+$S[x]$ such that $f(x) + g(x) = 0_R$.  As a direct result, for any $f(\alpha)$
+in $S[\alpha]$ there exists a $g(\alpha)$ such that
+$f(\alpha) + g(\alpha) = 0_R$.
+\\
+\\
+Thus, $S[\alpha]$ is a subring of $R$.
+
 \item TODO

### 2019-10-02 hw5/MSimonsHW5.tex
hw5
Correcting HW 5 number 1

@@
 
-\item To prove $\varphi_{\alpha}$ is closed under addition, first let $f$, $g$
-be any elements of $S[x]$.  We know that $f+g$ is also an element of
-$S[x]$ because the coefficients of $f$ and $g$ are elements of $S$, which is a
-ring.  This implies that the coefficients of $f$ and $g$ are closed under
-addition, so the coefficients of $f+g$ are also in $S$.
-\\ \\
-With this having be said, we can prove $\varphi_{\alpha}$ is closed under addition
-as such:
+\item Assume that if $f(x)$, $g(x)$, $s(x)$, $d(x)$, $p(x)$ in $S[x]$ satisfy
 \[
-\varphi_{\alpha}(f+g) = (f+g)(\alpha) = f(\alpha) + g(\alpha)
-= \varphi_{\alpha}(f) + \varphi_{\alpha}(g)
+f(x) + g(x) = s(x)
+\] \[
+f(x) - g(x) = d(x)
+\] \[
+f(x)g(x) = p(x)
 \]
-We know $f \cdot g$ is an element of $S[x]$ since $S$ is closed under multiplication,
-so the coefficients of $f \cdot g$ are elements of $S$.
-\\ \\
-We can prove $\varphi_{\alpha}$ is closed under multiplication as such:
+then
 \[
-\varphi_{\alpha}(f \cdot g) = (f \cdot g)(\alpha) = f(\alpha) \cdot g(\alpha)
-= \varphi_{\alpha}(f) \cdot \varphi_{\alpha}(g)
+\] \[
+f(\alpha) + g(\alpha) = s(\alpha)
+\] \[
+f(\alpha) - g(\alpha) = d(\alpha)
+\] \[
+f(\alpha)g(\alpha) = p(\alpha)
 \]
-Thus, $\varphi_{\alpha}$ is a ring homomorphism.
+We can prove that $\phi_{\alpha}$ is closed under addition as such:
+\[
+\phi_{\alpha}(f) + \phi_{\alpha}(g) = f(\alpha) + g(\alpha) = s(\alpha) = \phi_{\alpha}(s)
+\] \[
+\phi_{\alpha}(f) - \phi_{\alpha}(g) = f(\alpha) - g(\alpha) = d(\alpha) = \phi_{\alpha}(d)
+\]
+We can prove that $\phi_{\alpha}$ is closed under multiplication as such:
+\[
+\phi_{\alpha}(f)\phi_{\alpha}(g) = f(\alpha)g(\alpha) = p(\alpha) = \phi_{\alpha}(p)
+\]
+Thus, $\phi_{\alpha}$ is a ring homomorphism.
 
@@
 
-\item TODO
+\item Let $(a_0 + a_{1}x + ... + a_{n}x^n)$, $(b_0 + b_{1}x + ... + b_{n}x^n)$
+be elements of $R_{1}[x]$.
+\\
+\\
+We can prove $G$ is closed under addition as such:
+\[
+G((a_0 + a_{1}x + ... + a_{n}x^{n}) + (b_0 + b_{1}x + ... + b_{n}x^{n}))
+\] \[
+= G(a_0 + a_{1}x + ... + a_{n}x^n + b_0 + b_{1}x + ... + b_{n}x^{n})
+\] \[
+= F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n} + F(b_{0}) + F(b_{1})x + ... + F(b_{n})x^{n}
+\] \[
+= (F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n}) + (F(b_{0}) + F(b_{1})x + ... + F(b_{n})x^{n})
+\] \[
+= G(a_0 + a_{1}x + ... + a_{n}x^{n}) + G(b_0 + b_{1}x + ... + b_{n}x^{n})
+\]
+We can prove $G$ is closed under multiplication as such:
+\[
+G((a_0 + a_{1}x + ... + a_{n}x^{n}) (b_0 + b_{1}x + ... + b_{n}x^{n}))
+\] \[
+= G (a_{0}b_{0} + ... + a_{n}b_{m}x^{n+m})
+\] \[
+= F(a_{0}b_{0}) + ... + F(a_{n}b_{m})x^{n+m}
+\] \[
+= F(a_{0})F(b_{0}) + ... + F(a_{n})F(b_{m})x^{n+m}
+\] \[
+= (F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n})(F(b_{0}) + F(b_{1})x + ... + F(b_{m})x^{m})
+\] \[
+= G(a_0 + a_{1}x + ... + a_{n}x^{n}) G(b_0 + b_{1}x + ... + b_{n}x^{n})
+\]
+Therefore $G$ is also a a ring homomorphism.
 

### 2019-10-02 hw5/MSimonsHW5.tex
corrected HW 5 problem 2

@@
 \]
-then
+then, for any $\alpha$ in $R$,
 \[
@@
 
-\item Let $f(\alpha)$, $g(\alpha)$ be any elements in $S[\alpha]$.  By the
-definition of $S[\alpha]$, $f(x)$, $g(x)$ as elements of $S[x]$.  Since $S[x]$
-is a ring homomorphism, $(f+g)(x)$ is an element of $S[x]$.  If $(f+g)(x)$ is an
-element of $S[x]$, then $(f+g)(\alpha)$ is an element of $S[\alpha]$ and
-$S[\alpha]$ is closed under addition.
+\item Let $f(\alpha)$, $g(\alpha)$ be elements in $S[\alpha]$.  This implies
+that $f(x)$ and $g(x)$ are elements of $S[x]$.  Since $S$ is a ring, its
+elements are closed under addition, implying that $S[x]$ is closed under
+addition as well.  Let $f(x) + g(x) = s(x)$ and $f(x) - g(x) = d(x)$.  Since
+$s(x)$ and $d(x)$ are in $S[x]$, $s(\alpha) = f(\alpha) + g(\alpha)$ and
+$d(\alpha) = f(\alpha) - g(\alpha)$ are elements of $S[\alpha]$ and $S[\alpha]$
+is closed under addition.
 \\
 \\
-Similarly, $f(x)g(x)$ is an element of $S[x]$.  This implies that
-$f(\alpha)g(\alpha)$ is an element of $S[\alpha]$ and so $S[\alpha]$ is
-closed under multiplication.
-\\
-\\
-For $S[\alpha]$ to be a subring of $R$, $0_R$ must be an element of $S[\alpha]$.
-Define the function $f:S[x] \rightarrow R$ by $f(x) = 0_R$.  As such,
-$f(\alpha) = 0_R$ is an element of $S[\alpha]$.
-\\
-\\
-Let $f(x) = a_0 + a_{1}x + ... + a_{n}x^n$ be any element of $S[x]$.
-By definition, $a_i$ is an element of $R$ for all non-negative integers $i$, and
-for all $a_i$, there exists a $b_i$ in $R$ such that $a_i + b_i = 0_R$.
-Therefore, there exists a function $g(x) = b_0 + b_{1}x + ... + b_{n}x^n$ in
-$S[x]$ such that $f(x) + g(x) = 0_R$.  As a direct result, for any $f(\alpha)$
-in $S[\alpha]$ there exists a $g(\alpha)$ such that
-$f(\alpha) + g(\alpha) = 0_R$.
+Similarly, since $S$ is closed under multiplication, we can assume $p(x) = f(x)g(x)$
+is an element of $S[x]$.  Therefore $p(\alpha) = f(\alpha)g(\alpha)$ is an
+element of $S[\alpha]$ and $S[alpha]$ is closed under multiplication.
 \\

### 2019-10-02 hw3/MSimonsHW3.tex
problem 3 hw 3
hw3
Fixing some typos in HW 3

@@
 multiplication.  Let $a = \frac{m}{2}$ and $b = \frac{n}{2}$ for some integers
-$m$, $n$.  We know that $ab = \frac{mn}/4$.  Assume $m$ and $n$ are both odd and
+$m$, $n$.  We know that $ab = \frac{mn}{4}$.  Assume $m$ and $n$ are both odd and
 that $m = 2x + 1$ and $n = 2y + 1$ for some integers $x$, $y$.  Therefore,
@@
 \[
-a + b = \frac{m}{2x+1} + frac{n}{2y+1} = \frac{m(2y+1) + 2(nx+1)}{2(2xy+x+y)+1}
+a + b = \frac{m}{2x+1} + \frac{n}{2y+1} = \frac{2my+2nx+m+n}{2(2xy+x+y)+1}
 \]
@@
 \]
-There exists an $0$ element in the set such that:
+Next, we can prove the existence of $0_S$ by letting $0_S = 0$:
 \[
-a + 0 = \frac{m}{2x+1} + \frac{0}{1} = \frac{m}{2x+1} = a
-= \frac{0}{1} + \frac{m}{2x+1} = 0 + a
+a + 0_S = a + 0 = a = 0 + a = 0_S + a
 \]
-There is a solution to $a + x = 0$.  Let $x = \frac{-m}{2x+1}$:
+There is a solution to $a + x = 0$.  Let $x = \frac{-m}{2x+1}$ for any integers $m$, $x$:
 \[
@@
 
-\item TODO
+\item The set is not a ring as it is not closed under multiplication.\\
+Let $\frac{m}{6x+3}$, $\frac{n}{6y+4}$ be elements of the set for some integers
+$m$, $n$, $x$, and $y$.  As such,
+\[
+\frac{m}{6x+3}\cdot\frac{n}{6y+4} = \frac{mn}{6(6xy+4x+3y+2)}
+\]
 
-\item TODO
+\item
 
@@
 \\
-Let $m$ be the greatest common denominator of $a$, $b$, $c$, and $d$.
+Let $m$ be the greatest common divisor of $a$, $b$, $c$, and $d$.
 Let $a = mx$, $b = my$, $c = mz$, and $d = mw$ for some integers
@@
 denominator and $m^2$ is also a common denominator, $m^2 \leq m$ and this is
-only possible if $m = 1$.  Therefore, the greatest common denominator of
+only possible if $m = 1$.  Therefore, the greatest common divisor of
 $a$, $b$, $c$, and $d$ is 1.  If this is the case, $ad-bc$ must be $\pm1$ since

### 2019-10-02 hw3/MSimonsHW3.tex
Hw3 number 4

@@
 
-\item
+\item Assume $a$, $b$ are elements in $R_1 \cap R_2$.  This implies $a$, $b$ are
+in $R_1$.  Since $R_1$ is a subring, $a+b$ is in $R_1$.  Similarly, $a$, $b$ are
+in $R_2$ and $a+b$ is in $R_2$ as $R_2$ is also a subring.  Since $a+b$ is in
+$R_1$ and $R_2$, $a+b$ is in $R_1 \cap R_2$ and $R_1 \cap R_2$ is closed
+under addition.
+\\
+\\
+Since $R_1$ and $R_2$ are subrings, $ab$ is in $R_1$ and $ab$ is in $R_2$.
+Therefore $ab$ is in $R_1 \cap R_2$ and $R_1 \cap R_2$ is closed under
+multiplication.
+\\
+\\
+Thus, $R_1 \cap R_2$ is a subring of $R$ (and therefore a ring).
+\\
+\\
+$R_1 \cup R_2$ is not necessarily a ring.  Let $R_1$ and $R_2$ be
+ subrings of $R$ such that $R_2$ is not a subring of $R_1$.  Let $a$ be an
+ element of $R_1$, but not of $R_2$.  Let $b$ be any element of $R_2$.
+ \\
+ \\
+ If $R_1 \cup R_2$ is a ring, $a+b$ is in $R_1 \cup R_2$.  By definition of
+ union, $a+b$ is in $R_1$ or $a+b$ is in $R_2$.  If $a+b$ is in $R_1$, then
+ $(a+b)-a$ is also in $R_1$ (since $R_1$ is closed under addition).  However,
+ this implies $b$ is in $R_1$.  If any element in $R_2$ is an element of $R_1$,
+ then $R_2$ is a subring of $R_1$, which is a contradiction.  If $a+b$ is in
+ $R_2$, then $(a+b)-b$ is also in $R_2$.  This implies that $a$ is in $R_2$,
+ which is another contradiction.  Therefore, if two subrings exist such that
+ neither is a subset of the other, their union is not a ring.
 

### 2019-10-22 hw6/MSimonsHW6.tex
Starting HW 6
HW6 problem 1

--- 2019-09-26 hw4/MSimonsHW4.tex
@@
 \documentclass{article}
-\title{Homework 4}
+\title{Homework 6}
 \author{Madilyn Simons}
@@
 
-\item TODO
-
-\item TODO
-
-\item TODO
-
-\item TODO
-
-\item TODO
-
-\item TODO
+\item To prove that "is an associate of" is an equivalence relation on $R$, we
+must show that it is reflexive, symmetric, and transitive.
+\\
+\\
+First, since $R$ is a commutative ring, there exists some identity element in
+$R$, $1_R$, such that $a1_R = a$.  We can say that $1_R$ is a unit since
+$1_{R} \dot 1_{R} = 1_{R}$.  Since $a1_R = a$, $a$ is an associate of $a$
+and "is an associate of" is reflexive.
+\\
+\\
+Next, let $a$, $b \in R$ such that $a$ is an associate of $b$.  Therefore,
+there exist some unit, $u$, in $R$ sucht that $au = b$.  Since $u$ is a unit,
+there also exists some unit $v \in R$ such that $uv = 1_R$.
+\\
+\\
+If $a = bu$, then
+\[
+av = (bu)v
+\] \[
+av = buv
+\] \[
+av = b(uv)
+\] \[
+av = b1_{R}
+\] \[
+av = b
+\]
+Therefore, $b$ is an associate of $a$ and "is an associate of" is reflexive.
+\\
+\\
+Finally, let $a$ be an associate of $b$ and let $b$ be an associate of $c$ for
+some elements $a$, $b$, $c \in R$.  Therefore, $a = bu$ and $b = cv$ for some
+units $u$, $v \in R$.
+\\
+\\
+We notice that
+\[
+a = bu
+\] \[
+a = (cv)u
+\] \[
+a = c(vu)
+\]
+We know that $vu$ is a unit because there exists some
+$v^{-1}$, $u^{-1} \in R$ such that $vv^{-1} = 1_R$ and $uu^{-1} = 1_R$ since
+$v$ and $u$ are units.  Thus, $(vu)(v^{-1}u^{-1}) = (vv^{-1})(uu^{-1}) = 1_R$
+and so $vu$ is a unit.  Since $vu$ is a unit, $a$ is an associate of $c$ and
+"is an associate of" is transitive.
 

### 2019-10-24 hw6/MSimonsHW6.tex
hw6 question 2b

@@
 \documentclass{article}
+\usepackage{amsmath,amssymb}
+\newcommand{\Z}{\mathbb{Z}}
 \title{Homework 6}
@@
 $R$, $1_R$, such that $a1_R = a$.  We can say that $1_R$ is a unit since
-$1_{R} \dot 1_{R} = 1_{R}$.  Since $a1_R = a$, $a$ is an associate of $a$
+$(1_{R})  (1_{R}) = 1_{R}$.  Since $a1_R = a$, $a$ is an associate of $a$
 and "is an associate of" is reflexive.
@@
 
+\item
+\begin{enumerate}
+\item There are 4 different quadratic polynomial in $(\Z/2\Z)[x]$:
+\[
+x^2
+\] \[
+x^2 + 1
+\] \[
+x^2 + x
+\] \[
+x^2 + x + 1
+\]
+Let $f(x)$ be any quadratic polynomial in $(\Z/2\Z)[x]$.  We know that
+If $f(x) = x^2$, then $f(x)$ is reducible because $0$ is a root.
+If $f(x) = x^2 + 1$, then $f(x)$ is reducible because $1$ is a root.
+If $f(x) = x^2 + x$, then $f(x)$ is reducible because $1$ is a root.
+\\ \\
+If $f(x) = x^2 + x + 1$, then $f(x)$ is irreducible because $f(x)$ has no roots
+in $(\Z/2\Z)[x]$:
+\[
+f(0) = 0^2 + 0 + 1 = 1
+\] \[
+f(1) = 1^1 + 1 + 1 = 3 = 1
+\]
+\\
+Therefore the only irreducible quadratic polynomial in $(\Z/2\Z)[x]$ is
+$x^2 + x + 1$.
+
+\item TODO
+\end{enumerate}
+
 \end{enumerate}

### 2019-10-24 hw6/MSimonsHW6.tex
hw6 question 2bcd
the rest of hw6
Fixed some typos in HW6

@@
 Next, let $a$, $b \in R$ such that $a$ is an associate of $b$.  Therefore,
-there exist some unit, $u$, in $R$ sucht that $au = b$.  Since $u$ is a unit,
+there exist some unit, $u$, in $R$ such that $au = b$.  Since $u$ is a unit,
 there also exists some unit $v \in R$ such that $uv = 1_R$.
@@
 Let $f(x)$ be any quadratic polynomial in $(\Z/2\Z)[x]$.  We know that
-If $f(x) = x^2$, then $f(x)$ is reducible because $0$ is a root.
+if $f(x) = x^2$, then $f(x)$ is reducible because $0$ is a root.
 If $f(x) = x^2 + 1$, then $f(x)$ is reducible because $1$ is a root.
@@
 
-\item TODO
+\item No, because $f(1) = 0$.
+\item Yes, because $g(0) = g(1) = 1$.
+\item Yes, because $h(0) = h(1) = 1$.
+
 \end{enumerate}
+
+\item By Eisenstein's Criterion, $p(x)$ is irreducible.  Let $q = 2$.  Since
+$q$ is a prime that divides all of the coefficients except for the leading
+coefficient and $q^2$ does not divide 34, $p(x)$ is irreducible.
+
+\item Let $p = 11$.  Then $\overline{q}(x) = x^4 + 7x + 5$.
+Since $\overline{q}(x)$ is irreducible in $(\Z/p\Z)[x]$ and
+$p$ does not divide the leading coefficient of $q(x)$,
+$q(x)$ is irreducible.
 

### 2019-10-30 hw7/MSimonsHW7.tex
hw7 problem 2

--- 2019-10-22 hw6/MSimonsHW6.tex
@@
 \documentclass{article}
-\title{Homework 6}
+\usepackage{amsmath,amssymb}
+\newcommand{\Z}{\mathbb{Z}}
+\title{Homework 7}
 \author{Madilyn Simons}
@@
 
-\item To prove that "is an associate of" is an equivalence relation on $R$, we
-must show that it is reflexive, symmetric, and transitive.
-\\
-\\
-First, since $R$ is a commutative ring, there exists some identity element in
-$R$, $1_R$, such that $a1_R = a$.  We can say that $1_R$ is a unit since
-$1_{R} \dot 1_{R} = 1_{R}$.  Since $a1_R = a$, $a$ is an associate of $a$
-and "is an associate of" is reflexive.
-\\
-\\
-Next, let $a$, $b \in R$ such that $a$ is an associate of $b$.  Therefore,
-there exist some unit, $u$, in $R$ sucht that $au = b$.  Since $u$ is a unit,
-there also exists some unit $v \in R$ such that $uv = 1_R$.
-\\
-\\
-If $a = bu$, then
-\[
-av = (bu)v
-\] \[
-av = buv
-\] \[
-av = b(uv)
-\] \[
-av = b1_{R}
-\] \[
-av = b
-\]
-Therefore, $b$ is an associate of $a$ and "is an associate of" is reflexive.
-\\
-\\
-Finally, let $a$ be an associate of $b$ and let $b$ be an associate of $c$ for
-some elements $a$, $b$, $c \in R$.  Therefore, $a = bu$ and $b = cv$ for some
-units $u$, $v \in R$.
-\\
-\\
-We notice that
-\[
-a = bu
-\] \[
-a = (cv)u
-\] \[
-a = c(vu)
-\]
-We know that $vu$ is a unit because there exists some
-$v^{-1}$, $u^{-1} \in R$ such that $vv^{-1} = 1_R$ and $uu^{-1} = 1_R$ since
-$v$ and $u$ are units.  Thus, $(vu)(v^{-1}u^{-1}) = (vv^{-1})(uu^{-1}) = 1_R$
-and so $vu$ is a unit.  Since $vu$ is a unit, $a$ is an associate of $c$ and
-"is an associate of" is transitive.
+\item TODO
+
+\item If $p = 2$, then $\overline{f}(x) = x^5 + x^2 + 1$ in $\mathbb{Z}_{p}[x]$.
+Since $\overline{f}(0) = \overline{f}(1) = 1$, $\overline{f}(x)$ is
+irreducible in $\mathbb{Z}_{p}[x]$.  Therefore, by Theorem 4.25, $f(x)$ is
+irreducible in $\mathbb{Q}[x]$.
+
+\item TODO
 

### 2019-10-30 hw7/MSimonsHW7.tex
added to hw7 problem 2
hw7 problem 3

@@
 
-\item If $p = 2$, then $\overline{f}(x) = x^5 + x^2 + 1$ in $\mathbb{Z}_{p}[x]$.
+\item Let $f(x) = x^5 - 4x^4 + 4d^3 + 3x^2 -26x + 21$.
+If $p = 2$, then $\overline{f}(x) = x^5 + x^2 + 1$ in $\mathbb{Z}_{p}[x]$.
 Since $\overline{f}(0) = \overline{f}(1) = 1$, $\overline{f}(x)$ is
-irreducible in $\mathbb{Z}_{p}[x]$.  Therefore, by Theorem 4.25, $f(x)$ is
+irreducible in $\mathbb{Z}_{p}[x]$.  Therefore, $f(x)$ is
 irreducible in $\mathbb{Q}[x]$.
 
-\item TODO
+\item
+\begin{enumerate}
+\item
+Since $-1 + 3i$ is a root of $f(x)$, $-1 - 3i$ is a root of $f(x)$.
+Therefore
+\[
+f(x) = (x + 1 + 3i)(x + 1 - 3i)(h(x)) = (x^2 + 2x + 10)(h(x))
+\] for
+some polynomial $h(x)$.
+By division,
+\[h(x) = f(x) / (x^2 + 2x + 10) = x^4 + x^2 - 6
+\]
+Thus,
+\[f(x) = (x^2 + 2x + 10)(x^4 + x^2 - 6) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2)
+\]
+We know that $(x^2 + 2x + 10)$ and $(x^2 - 2)$ are irreducible in $\mathbb{Q}[x]$
+by Eisenstein's Criterion for prime $p = 2$, and $(x^2 + 3)$ is irreducible
+in $\mathbb{Q}[x]$ for prime $p = 3$.  Therefore, the irreducible
+factorization of $f(x)$ in $\mathbb{Q}[x]$ is
+\[
+f(c) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2)
+\]
+
+\item
+In $\mathbb{R}[x]$,
+\[f(x) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2)
+= (x^2 + 2x + 10)(x^2 + 3)(x + \sqrt{2})(x - \sqrt{2})
+\]
+We know that $(x^2 + 2x + 10)$ and $(x^2 + 3)$ are irreducible $\mathbb{R}[x]$
+because a polynomial of the form $f(x) = ax^2 + bx + c$ is irreducible in
+$\mathbb{R}[x]$ if $b^2 - 4ac < 0$.  Therefore, the irreducible factorization
+of $f(x)$ in $\mathbb{R}[x]$ is
+\[
+(x^2 + 2x + 10)(x^2 + 3)(x + \sqrt{2})(x - \sqrt{2})
+\]
+
+\item
+In $\mathbb{C}[x]$, the irreducible factorization of $f(x)$ is
+\[
+f(x) = (x + 1 + 3i)(x + 1 - i)(x + \sqrt{3}i)(x - \sqrt{3}i)(x + \sqrt{2})(x - \sqrt{2})
+\]
+We know that each of these polynomials are irreducible in $\mathbb{C}[x]$ because
+they all have degree 1.
 
 \end{enumerate}
+\end{enumerate}
 \end{document}

### 2019-10-31 hw5/MSimonsHW5.tex
correcting hw5 number 3

@@
 \]
-We can prove that $\phi_{\alpha}$ is closed under addition as such:
+We can prove that $\phi_{\alpha}$ preserves addition as such:
 \[
@@
 \]
-We can prove that $\phi_{\alpha}$ is closed under multiplication as such:
+We can prove that $\phi_{\alpha}$ preserves multiplication as such:
 \[
@@
 that $f(x)$ and $g(x)$ are elements of $S[x]$.  Since $S$ is a ring, its
-elements are closed under addition, implying that $S[x]$ is closed under
+elements are closed under addition, implying that $S[x]$ preserves
 addition as well.  Let $f(x) + g(x) = s(x)$ and $f(x) - g(x) = d(x)$.  Since
@@
 $d(\alpha) = f(\alpha) - g(\alpha)$ are elements of $S[\alpha]$ and $S[\alpha]$
-is closed under addition.
+preserves addition.
 \\
 \\
-Similarly, since $S$ is closed under multiplication, we can assume $p(x) = f(x)g(x)$
+Similarly, since $S$ preserves multiplication, we can assume $p(x) = f(x)g(x)$
 is an element of $S[x]$.  Therefore $p(\alpha) = f(\alpha)g(\alpha)$ is an
-element of $S[\alpha]$ and $S[alpha]$ is closed under multiplication.
+element of $S[\alpha]$ and $S[alpha]$ preserves multiplication.
 \\
@@
 
-\item Let $(a_0 + a_{1}x + ... + a_{n}x^n)$, $(b_0 + b_{1}x + ... + b_{n}x^n)$
+\item Let $a(x) = (a_0 + a_{1}x + ... + a_{n}x^n)$, $b(x) = (b_0 + b_{1}x + ... + b_{n}x^m)$
 be elements of $R_{1}[x]$.
-\\
-\\
-We can prove $G$ is closed under addition as such:
-\[
-G((a_0 + a_{1}x + ... + a_{n}x^{n}) + (b_0 + b_{1}x + ... + b_{n}x^{n}))
-\] \[
-= G(a_0 + a_{1}x + ... + a_{n}x^n + b_0 + b_{1}x + ... + b_{n}x^{n})
-\] \[
-= F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n} + F(b_{0}) + F(b_{1})x + ... + F(b_{n})x^{n}
-\] \[
-= (F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n}) + (F(b_{0}) + F(b_{1})x + ... + F(b_{n})x^{n})
-\] \[
-= G(a_0 + a_{1}x + ... + a_{n}x^{n}) + G(b_0 + b_{1}x + ... + b_{n}x^{n})
-\]
-We can prove $G$ is closed under multiplication as such:
-\[
-G((a_0 + a_{1}x + ... + a_{n}x^{n}) (b_0 + b_{1}x + ... + b_{n}x^{n}))
-\] \[
-= G (a_{0}b_{0} + ... + a_{n}b_{m}x^{n+m})
-\] \[
-= F(a_{0}b_{0}) + ... + F(a_{n}b_{m})x^{n+m}
-\] \[
-= F(a_{0})F(b_{0}) + ... + F(a_{n})F(b_{m})x^{n+m}
-\] \[
-= (F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n})(F(b_{0}) + F(b_{1})x + ... + F(b_{m})x^{m})
-\] \[
-= G(a_0 + a_{1}x + ... + a_{n}x^{n}) G(b_0 + b_{1}x + ... + b_{n}x^{n})
-\]
+\\ \\
+Since $F$ is a ring homomorphism, we can prove $G$ preserves addition as such:
+
+\begin{align*}
+G(a(x) + b(x)) &= G((a_0 + a_{1}x + ... + a_{n}x^{n}) + (b_0 + b_{1}x + ... + b_{m}x^{m})) \\
+&= G(a_0 + a_{1}x + ... + a_{n}x^n + b_0 + b_{1}x + ... + b_{m}x^{m}) \\
+&= F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n} + F(b_{0}) + F(b_{1})x + ... + F(b_{m})x^{m} \\
+&= (F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n}) + (F(b_{0}) + F(b_{1})x + ... + F(b_{m})x^{m}) \\
+&= G(a_0 + a_{1}x + ... + a_{n}x^{n}) + G(b_0 + b_{1}x + ... + b_{m}x^{m}) \\
+&= G(a(x)) + G(b(x))
+\end{align*}
+
+We can prove $G$ preserves multiplication as such:
+\begin{align*}
+G((ab)(x)) &= G((a_0 + a_{1}x + ... + a_{n}x^{n})(b_0 + b_{1}x + ... + b_{m}x^{m})) \\
+&= G(a_{0}b_{0} + (a_{0}b_{1} + a_{1}b_{0})x + (a_{0}b_{2} + a_{1}b_{1} + a_{2}b_{0})x^2 + ... + a_{n}b_{m}x^{x+m}) \\
+&= F(a_{0}b_{0}) + F(a_{0}b_{1} + a_{1}b_{0})x + F(a_{0}b_{2} + a_{1}b_{1} + a_{2}b_{0})x^2 + ... + F(a_{n}b_{m})x^{x+m} \\
+&= (F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n})(F(b_{0}) + F(b_{1})x + ... + F(b_{m})x^{m}) \\
+&= G(a_0 + a_{1}x + ... + a_{n}x^{n})G(b_0 + b_{1}x + ... + b_{m}x^{m}) \\
+&= G(a(x))G(b(x))
+\end{align*}
+
 Therefore $G$ is also a a ring homomorphism.

### 2019-10-31 hw5/MSimonsHW5.tex
Correcting problem 1 from hw 5
Correcting number 2 hw 5

@@
 \]
-We can prove that $\phi_{\alpha}$ preserves addition as such:
+We can prove that $\varphi_{\alpha}$ preserves addition as such:
 \[
-\phi_{\alpha}(f) + \phi_{\alpha}(g) = f(\alpha) + g(\alpha) = s(\alpha) = \phi_{\alpha}(s)
-\] \[
-\phi_{\alpha}(f) - \phi_{\alpha}(g) = f(\alpha) - g(\alpha) = d(\alpha) = \phi_{\alpha}(d)
+\varphi_{\alpha}(f) + \varphi_{\alpha}(g) = f(\alpha) + g(\alpha) = s(\alpha) = \varphi_{\alpha}(s) = \varphi_{\alpha}(f+g)
 \]
-We can prove that $\phi_{\alpha}$ preserves multiplication as such:
+We can prove that $\varphi_{\alpha}$ preserves multiplication as such:
 \[
-\phi_{\alpha}(f)\phi_{\alpha}(g) = f(\alpha)g(\alpha) = p(\alpha) = \phi_{\alpha}(p)
+\varphi_{\alpha}(f)\varphi_{\alpha}(g) = f(\alpha)g(\alpha) = p(\alpha) = \varphi_{\alpha}(p) = \varphi_{\alpha}(fg)
 \]
-Thus, $\phi_{\alpha}$ is a ring homomorphism.
+Thus, $\varphi_{\alpha}$ is a ring homomorphism.
 
-\item Let $f(\alpha)$, $g(\alpha)$ be elements in $S[\alpha]$.  This implies
-that $f(x)$ and $g(x)$ are elements of $S[x]$.  Since $S$ is a ring, its
-elements are closed under addition, implying that $S[x]$ preserves
-addition as well.  Let $f(x) + g(x) = s(x)$ and $f(x) - g(x) = d(x)$.  Since
+\item Let $f(\alpha)$, $g(\alpha)$ be elements in $S[\alpha]$, where
+$f(x)$ and $g(x)$ are elements of $S[x]$.
+Let $f(x) + g(x) = s(x)$ and $f(x) - g(x) = d(x)$.  Since
 $s(x)$ and $d(x)$ are in $S[x]$, $s(\alpha) = f(\alpha) + g(\alpha)$ and
 $d(\alpha) = f(\alpha) - g(\alpha)$ are elements of $S[\alpha]$ and $S[\alpha]$
-preserves addition.
+preserves addition and subtraction.
 \\
 \\
-Similarly, since $S$ preserves multiplication, we can assume $p(x) = f(x)g(x)$
+Similarly, since $S$ preserves multiplication, $p(x) = f(x)g(x)$
 is an element of $S[x]$.  Therefore $p(\alpha) = f(\alpha)g(\alpha)$ is an
-element of $S[\alpha]$ and $S[alpha]$ preserves multiplication.
+element of $S[\alpha]$ and $S[\alpha]$ preserves multiplication.
 \\

### 2019-10-31 hw7/MSimonsHW7.tex
hw 7 problem 1
Cleaned up hw7 and updated pdf for hw5:

@@
 
-\item TODO
+\item If $f(x) = x^7 - 7x + 20$, then
+\[
+f(x+1) = x^7 + 7x^6 + 21x^5 + 35x^4 + 35x^3 + 21x^2 + 14
+\]
+By Eisenstein's Criterion, $f(x + 1)$ is irreducible in $\mathbb{Q}[x]$ for $p = 7$,
+and so $f(x)$ is irreducible in $\mathbb{Q}[x]$.
 
@@
 \item
-Since $-1 + 3i$ is a root of $f(x)$, $-1 - 3i$ is a root of $f(x)$.
+Since $-1 + 3i$ is a root of $f(x)$, $-1 - 3i$ is also a root of $f(x)$.
 Therefore
@@
 some polynomial $h(x)$.
+\\ \\
 By division,
@@
 by Eisenstein's Criterion for prime $p = 2$, and $(x^2 + 3)$ is irreducible
-in $\mathbb{Q}[x]$ for prime $p = 3$.  Therefore, the irreducible
+in $\mathbb{Q}[x]$ by Eisenstein's Criterion for prime $p = 3$.
+Therefore, the irreducible
 factorization of $f(x)$ in $\mathbb{Q}[x]$ is

### 2019-11-05 hw8/MSimonsHW8.tex
Starting hw8
hw8 problem 1a

--- 2019-10-30 hw7/MSimonsHW7.tex
@@
 \newcommand{\Z}{\mathbb{Z}}
-\title{Homework 7}
+\title{Homework 8}
 \author{Madilyn Simons}
@@
 
+\item
+\begin{enumerate}
+
+\item Since $(x^7 + 25x^6 - 25x + 5)$ is a nonconstant polynomial in
+$\mathbb{Q}$, $\mathbb{Q}/(x^7 + 25x^6 - 25x + 5)$ is a field if and only if
+$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$.  We know that
+$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$ by Eisenstein's
+Criterion for prime $5$.  Thus, $\mathbb{Q}/(x^7 + 25x^6 - 25x + 5)$ is a field.
+
+\item TODO
 \item TODO
 
-\item If $p = 2$, then $\overline{f}(x) = x^5 + x^2 + 1$ in $\mathbb{Z}_{p}[x]$.
-Since $\overline{f}(0) = \overline{f}(1) = 1$, $\overline{f}(x)$ is
-irreducible in $\mathbb{Z}_{p}[x]$.  Therefore, by Theorem 4.25, $f(x)$ is
-irreducible in $\mathbb{Q}[x]$.
+\end{enumerate}
 

### 2019-11-05 hw8/MSimonsHW8.tex
hw8 problem 1b
hw8 problem 1c

@@
 
-\item TODO
-\item TODO
+\item Consider $\mathbb{Z}/2\mathbb{Z}$.  If $f(x) = x^3 + 2x^2 - x + 1$, then
+$\overline{f}(x) = x^3 - x + 1$.  We know that $\overline{f}(x)$ is
+irreducible in $\mathbb{Z}/2\mathbb{Z}$ because
+$\overline{f}(0) = \overline{f}(1) = 1$.  Since $\overline{f}(x)$ is
+irreducible in $\mathbb{Z}/2\mathbb{Z}$, $f(x)$ is irreducible in $\mathbb{Q}$,
+which means that $\mathbb{Q}[x]/(x^3 + 2x^2 - x + 1)$ is a field.
+
+\item Only first-degree and second-degree polynomials can be irreducible in
+$\mathbb{R}[x]$.  Since $(x^5 + 42x^4 + \pi x^3 -1729x^2 + ln(2)x - 2019)$
+is a fifth-degree polynomial, it is reducible in $\mathbb{R}[x]$.  Therefore
+$\mathbb{R}[x]/(x^5 + 42x^4 + \pi x^3 -1729x^2 + ln(2)x - 2019)$ is NOT
+a field.
 

### 2019-11-05 hw8/MSimonsHW8.tex
hw8 problem 2a
hw8 prob 3

@@
 
+\item
+\begin{enumerate}
+\item
+Let $f(x) = x^3 + 2x + 1$.  We know that $f(x)$ is irreducible in
+$\mathbb{Z}/3\mathbb{Z}$ because $f(0) = f(1) = f(2) = 1$.  Therefore,
+$K$ is a field.
+
 \item TODO
@@
 \end{enumerate}
+
+\item To prove that $(a,b) = (d)$, first let us prove that $(a,b) \subseteq (d)$.
+Let $ar_1 + br_2$ be any element of $(a,b)$.  Since $d$ is the greatest common
+divisor of $a$ and $b$, $a = dx$ and $b = dy$ for some integers $x$ and $y$.
+Therefore, $ar_1 + br_2 = dxr_1 + dyr_2 = d(xr_{1} + dyr_{2})$, which is an
+element of $(d)$.  Thus, $(a,b) \subseteq (d)$. \\ \\
+Next, let us prove $(d) \subseteq (a,b)$.  Since $d$ is the greatest common
+divisor of $a$ and $b$, $d = au + bv$ for some integers $u$ and $v$.  Let
+$rd$ be any element of $(d)$.
+Therefore, $rd = r(au + bv) = rau + rbv = a(ru) + b(rv) \subseteq (a,b)$.
+Thus $(d) \subseteq (a,b)$. \\ \\
+Since $(d) \subseteq (a,b)$ and $(a,b) \subseteq (d)$, $(a,b) = (d)$.
+
+\end{enumerate}
 \end{document}

### 2019-11-07 hw8/MSimonsHW8.tex
hw 8 problem 4
Cleaning up hw8 problem 4
hw 8 problem 5

@@
 
+\item
+Let $a$, $b \in I$ such that
+\[a = 2a_0 + 2a_{1}x + ... + 2a_{n}x^n
+\]
+and
+\[b = 2b_0 + 2_b{1}x + ... 2b_{n}x^n
+\]
+and $a_i$ and $b_i$ are integers for all
+$i$.  We know that $I$ holds under subtraction because
+\begin{align*}
+a - b &= (2a_0 + 2a_{1}x + ... + 2a_{n}x^{n}) - (2b_0 + 2_b{1}x + ... 2b_{n}x^n) \\
+&= (2a_0 - 2b_0) + (2a_{1} - 2b_{1})x + ... + (2a_{n} - 2b_{n})x^n \\
+&= 2(a_0 - b_0) + 2(a_{1} - b_{1})x + ... + 2(a_{n} - b_{n})x^n \\
+\end{align*}
+
+Next let
+\[
+c = c_0 + c_{1}x + ... + c_{n}x^n
+\]
+be an element of $\mathbb{Z}[x]$.
+We know that $I$ absorbs multiplication because
+\begin{align*}
+ca &= (c_0 + c_{1}x + ... + c_{n}x^{n})(2a_0 + 2a_{1}x + ...+ 2a_{n}x^{n}) \\
+&= 2(c_0 + c_{1}x + ... + c_{n}x^{n})(a_0 + a_{1}x + ... + a_{n}x^{n}) \\
+&= 2(c_{0}a_{0} + (c_{0}a_{1} + c_{1}a_{0})x + (c_{0}a_{2} + c_{1}a_{1} + c_{2}a_{0})x^{2}
++ ... + c_{n}a_{n}x^{n}) \\
+&= 2c_{0}a_{0} + 2(c_{0}a_{1} + c_{1}a_{0})x + 2(c_{0}a_{2} + c_{1}a_{1} + c_{2}a_{0})x^{2}
++ ... + 2c_{n}a_{n}x^{n} \\
+&\subseteq I
+\end{align*}
+and
+\begin{align*}
+ac &= (2a_0 + 2a_{1}x + ...+ 2a_{n}x^{n})(c_0 + c_{1}x + ... + c_{n}x^{n}) \\
+&= 2(a_0 + a_{1}x + ... + a_{n}x^{n})(c_0 + c_{1}x + ... + c_{n}x^{n}) \\
+&= 2(a_{0}c_{0} + (a_{0}c_{1} + a_{1}c_{0})x + (a_{0}c_{2} + a_{1}c_{1} + a_{2}c_{0})x^{2}
++ ... + a_{n}c_{n}x^{n}) \\
+&= 2a_{0}c_{0} + 2(a_{0}c_{1} + a_{1}c_{0})x + 2(a_{0}c_{2} + a_{1}c_{1} + a_{2}c_{0})x^{2}
++ ... + 2a_{n}c_{n}x^{n} \\
+&\subseteq I
+\end{align*}
+
+Therefore, $I$ is an ideal of $\mathbb{Z}[x]$.
+
+\item I claim that $I = (x^2 - 7)$.  Let $g(x)$, $f(x)$ be elements of $I$ such
+that $g(x) = f(x)q(x)+r(x)$ and the degree of $r(x)$ is less than the degree
+of $f(x)$.  We know that $g(x)$ is generated by $f(x)$ because
+\begin{align*}
+g(7) &= f(7)q(7) + r(7) \\
+0 &= 0*q(7) + r(7) \\
+0 &= 0 + r(7) \\
+0 &= r(7)
+\end{align*}
+Therefore $I$ is finitely generated.
+
 \end{enumerate}

### 2019-11-12 hw6/MSimonsHW6.tex
Fixed hw6 problem 1

@@
 
-\item To prove that "is an associate of" is an equivalence relation on $R$, we
+\item To prove that ``is an associate of'' is an equivalence relation on $R$, we
 must show that it is reflexive, symmetric, and transitive.
@@
 $(1_{R})  (1_{R}) = 1_{R}$.  Since $a1_R = a$, $a$ is an associate of $a$
-and "is an associate of" is reflexive.
+and ``is an associate of'' is reflexive.
 \\
@@
 Next, let $a$, $b \in R$ such that $a$ is an associate of $b$.  Therefore,
-there exist some unit, $u$, in $R$ such that $au = b$.  Since $u$ is a unit,
+there exist some unit, $u$, in $R$ such that $a = bu$.  Since $u$ is a unit,
 there also exists some unit $v \in R$ such that $uv = 1_R$.
@@
 \[
-av = (bu)v
-\] \[
-av = buv
-\] \[
-av = b(uv)
-\] \[
-av = b1_{R}
-\] \[
-av = b
+av = buv = b1_{R} = b
 \]
-Therefore, $b$ is an associate of $a$ and "is an associate of" is reflexive.
+Therefore, $b$ is an associate of $a$ and ``is an associate of'' is reflexive.
 \\
@@
 \[
-a = bu
-\] \[
-a = (cv)u
-\] \[
-a = c(vu)
+a = bu = cvu
 \]
@@
 and so $vu$ is a unit.  Since $vu$ is a unit, $a$ is an associate of $c$ and
-"is an associate of" is transitive.
+``is an associate of'' is transitive.
 

### 2019-11-12 hw6/MSimonsHW6.tex
Correcting 2c and 2d in hw6

@@
 \] \[
-f(1) = 1^1 + 1 + 1 = 3 = 1
+f(1) = 1^2 + 1 + 1 = 3 = 1
 \]
@@
 \item No, because $f(1) = 0$.
-\item Yes, because $g(0) = g(1) = 1$.
-\item Yes, because $h(0) = h(1) = 1$.
+\item No, because $g(x) = x^5 + x^4 + 1 = (x^2 + x +1)(x^3 - x + 1)$.
+\item Yes.  Since $h(x)$ does not have any roots, it is not divisible
+by a polynomial with degree 1.  Therefore, it can only be the product
+of an irreducible polynomial with degree 2 and an irreducible polynomial of
+degree 3.  The only irreducible polynomial with degree 2 in
+$\mathbb{Z}/2\mathbb{Z}$ in $x^2 + x + 1$.  Therefore, if $h(x)$ is reducible,
+then it is divisible by $\mathbb{Z}/2\mathbb{Z}$ in $x^2 + x + 1$.  However,
+$h(x)$ is NOT divisible by $\mathbb{Z}/2\mathbb{Z}$, so it must be irreducible.
 

### 2019-11-12 hw6/MSimonsHW6.tex
Fixing typo in hw6

@@
 degree 3.  The only irreducible polynomial with degree 2 in
-$\mathbb{Z}/2\mathbb{Z}$ in $x^2 + x + 1$.  Therefore, if $h(x)$ is reducible,
-then it is divisible by $\mathbb{Z}/2\mathbb{Z}$ in $x^2 + x + 1$.  However,
-$h(x)$ is NOT divisible by $\mathbb{Z}/2\mathbb{Z}$, so it must be irreducible.
+$\mathbb{Z}/2\mathbb{Z}$ is $x^2 + x + 1$.  Therefore, if $h(x)$ is reducible,
+then it is divisible by $x^2 + x + 1$ in $\mathbb{Z}/2\mathbb{Z}$.  However,
+$h(x)$ is NOT divisible by $x^2 + x + 1$, so it must be irreducible.
 

### 2019-11-12 hw6/MSimonsHW6.tex
Fixing typo in hw6

@@
 degree 3.  The only irreducible polynomial with degree 2 in
-$\mathbb{Z}/2\mathbb{Z}$ is $x^2 + x + 1$.  Therefore, if $h(x)$ is reducible,
-then it is divisible by $x^2 + x + 1$ in $\mathbb{Z}/2\mathbb{Z}$.  However,
+$(\Z/2\Z)[x]$ is $x^2 + x + 1$.  Therefore, if $h(x)$ is reducible,
+then it is divisible by $x^2 + x + 1$ in $(\Z/2\Z)[x]$.  However,
 $h(x)$ is NOT divisible by $x^2 + x + 1$, so it must be irreducible.

### 2019-11-14 hw7/MSimonsHW7.tex
hw 7 revisions

@@
 \]
-By Eisenstein's Criterion, $f(x + 1)$ is irreducible in $\mathbb{Q}[x]$ for $p = 7$,
+By Eisenstein's Criterion, for $p = 7$, $f(x + 1)$ is irreducible in $\mathbb{Q}[x]$,
 and so $f(x)$ is irreducible in $\mathbb{Q}[x]$.
 
-\item Let $f(x) = x^5 - 4x^4 + 4d^3 + 3x^2 -26x + 21$.
+\item Let $f(x) = x^5 - 4x^4 + 4x^3 + 3x^2 -26x + 21$.
 If $p = 2$, then $\overline{f}(x) = x^5 + x^2 + 1$ in $\mathbb{Z}_{p}[x]$.
-Since $\overline{f}(0) = \overline{f}(1) = 1$, $\overline{f}(x)$ is
-irreducible in $\mathbb{Z}_{p}[x]$.  Therefore, $f(x)$ is
-irreducible in $\mathbb{Q}[x]$.
+We know that $\overline{f}(x)$ is irreducible in $\mathbb{Z}_{p}[x]$ because
+since it has no roots, it is either irreducible or the product of an irreducible
+quadratic and an irreducible cubic.  However, the only irreducible quadratic
+in $\mathbb{Z}_{p}[x]$ is $x^2 + x + 1$, which does not divide $\overline{f}(x)$.
+Therefore, $f(x)$ is irreducible in $\mathbb{Q}[x]$.
 
@@
 By division,
-\[h(x) = f(x) / (x^2 + 2x + 10) = x^4 + x^2 - 6
+\[h(x) = f(x) / (x^2 + 2x + 10) = x^4 + x^2 - 6.
 \]
@@
 \[
-f(c) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2)
+f(c) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2).
 \]
@@
 \[
-(x^2 + 2x + 10)(x^2 + 3)(x + \sqrt{2})(x - \sqrt{2})
+(x^2 + 2x + 10)(x^2 + 3)(x + \sqrt{2})(x - \sqrt{2}).
 \]
@@
 \[
-f(x) = (x + 1 + 3i)(x + 1 - i)(x + \sqrt{3}i)(x - \sqrt{3}i)(x + \sqrt{2})(x - \sqrt{2})
+f(x) = (x + 1 + 3i)(x + 1 - 3i)(x + \sqrt{3}i)(x - \sqrt{3}i)(x + \sqrt{2})(x - \sqrt{2}).
 \]

### 2019-11-29 hw9/MSimonsHW9.tex
hw9 problems 1ab

\documentclass{article}
\usepackage{amsmath,amssymb}
\newcommand{\Z}{\mathbb{Z}}
\title{Homework 8}
\author{Madilyn Simons}
\date{}
\setlength{\parindent}{0pt}
\pdfpagewidth 8.5in
\pdfpageheight 11in

\usepackage{amssymb}
\usepackage{amsmath}

\begin{document}
\maketitle

\begin{enumerate}

\item
\begin{enumerate}

\item Let $I$ be a nonempty ideal in $F$ such that $I$ does not equal $F$.
Let $x \in F$ and $x \notin I$, let $a \in I$, and let $a^{-1}$ be the
multiplicative inverse of $a$.  If $a \in I$, then $ax \in I$ and
$a^{-1}ax \in I$.  However, $a^{-1}ax = 1_{F}x = x$ and $x \notin I$ so this
is a contradiction.

\item Since $f$ is a homomorphism of rings, the kernel of $f$ is an ideal
of $F$.  The only ideals of $F$ are $F$ and $(0)$.  If the kernel of
$f$ is $(0)$, then $f$ is injective.  If the kernel of $f$ is $F$, then
$f$ is the zero function.

\end{enumerate}

\end{enumerate}
\end{document}

### 2019-11-29 hw9/MSimonsHW9.tex
Starting problem 2 of hw9

@@
 
+\item TODO Rewrite this and replace $(q_{1}(x))$ with $(q_{i}(x))$
+
+First, assume $(p(x))$ is maximal.  Let
+$p(x) = q_{1}(x)q_{2}(x) ... q_{n}(x)$ be the prime factorization of $p(x)$.
+Therefore $(p(x)) \subset (q_{1}(x))$ since $q_{1}(x)$ divides $p(x)$.
+Since $(p(x))$ is maximal, either $(p(x)) = (q_{1}(x))$ or $F[x] = (q_{1}(x))$.
+\\ \\
+Assume $(p(x)) = (q_{1}(x))$.  Therefore $p(x)$ must be some divisor of
+$q_{1}(x)$ such that $q_{1}(x) = p(x)q_{2}^{-1}(x) ... q_{n}^{-1}(x)$.  This
+implies that $q_{2}(x), q_{3}(x), ..., q_{n}(x)$ are units, which are nonzero
+constants.  If $p(x)$ is the product of an irreducible polynomial $q_{1}(x)$
+and several nonzero constant polynomials, then $p(x)$ is irreducible.
+\\ \\
+Now assume $F[x] = (q_{1}(x))$.  If this is the case, then $q_{1}(x)$ must
+be a unit, which is a contradiction.
+\\ \\
+Therefore if $(p(x))$ is maximal, then $p(x)$ is irreducible.  Then the quotient
+ring $F[x]/(p(x))$ is all
+\\ \\
+Next, assume $p(x)$ is irreducible.  TODO
+
 \end{enumerate}

### 2019-11-30 hw9/MSimonsHW9.tex
hw9 prob 3
rough draft of hw9 -- needs to be cleaned up

@@
 \newcommand{\Z}{\mathbb{Z}}
-\title{Homework 8}
+\title{Homework 9}
 \author{Madilyn Simons}
@@
 \\ \\
-Therefore if $(p(x))$ is maximal, then $p(x)$ is irreducible.  Then the quotient
-ring $F[x]/(p(x))$ is all
-\\ \\
-Next, assume $p(x)$ is irreducible.  TODO
+Next, assume $p(x)$ is irreducible.  Since $p(x)$ is irreducible, the quotient
+ring $F[x]/(p(x))$ is a field and therefore $(p(x))$ is a maximal ideal.
+
+\item
+\begin{enumerate}
+\item
+By the Division Algorithm, $a(x) = b(x)q(x) + r(x)$ such that
+$0 \leq deg r(x) < deg b(x)$.  By Theorem 6.1, $b(x)q(x) \in I$ and
+$a(x) - b(x)q(x) = r(x) \in I$.
+
+\item Let $a(x)$ by any nonzero polynomial in $I$.  By the Division Algorithm,
+$a(x) = p(x)q(x) + r(x)$ such that $0 \leq deg r(x) < deg p(x)$.  However,
+$p(x)$ is of minimal degree, so $deg r(x) = 0$.  Therefore, $p(x)$ divides
+all $a(x) \in I$.
 
 \end{enumerate}
+
+\item
+\begin{enumerate}
+\item
+Let $I = \{f(x) \in F[x] | f(\alpha) = 0\}$.  We know that $I$ is an ideal of
+$F[x]$ because for all $f_{1}(x)$, $f_{2}(x) \in I$,
+\[
+f_{1}(\alpha) - f_{2}(\alpha) = 0-0 = 0
+\]
+So $f_{1}(x) - f_{2}(x) \in I$.  For all $g(x) \in F[x]$ and $f(x) \in I$,
+\[
+f(\alpha)g(\alpha) = 0*g(\alpha) = 0
+\] \[
+g(\alpha)f(\alpha) = g(\alpha)*0 = 0
+\]
+So $f(x)g(x) \in I$ and $g(x)f(x) \in I$, and $I$ is a proper ideal of $F[x]$.
+\\ \\
+Since $\alpha$ is a root of $p(x)$, $p(\alpha) = 0$ and $p(\alpha) \in I$.
+Because all ideals of $F[x]$ are principal ideals and $p(x)$ is irreducible,
+$I = (p(x))$ and all elements of $I$ are divisible by $p(x)$.  If $g(\alpha) = 0$,
+then $g(x) \in I$ and $p(x) | g(x)$.
+\\
+\\
+Next, assume $p(x) | g(x)$.  Then $g(x) = p(x)q(x)$ for some $q(x)$, and so
+\[
+g(\alpha) = p(\alpha)q(\alpha) = 0.
+\]
+Thus, $g(\alpha) = 0$ if and only if $p(x) | g(x)$.
+
+\item Let $I = \{f(x) \in \mathbb{Q} | f(\sqrt[7]{2}) = 0\}$.
+Let $p(x) = x^2 - 2$.  By Eisenstein's Criterion, $x^7 - 2$ is irreducible, and
+$p(\sqrt[7]{2}) = 0$ so $p(x) \in I$.  By problem $4a$, any nonzero
+$g(x) \in I$ must be divisible by $p(x)$, meaning that $deg$ $g \geq 7$.
+
+\item Let $g:F[x] \rightarrow F[\alpha]$ be a homomorphism of rings
+given by $g(f(x)) = f(\alpha)$ such that $f(x) \in F[x]$.  Then the kernel of
+$g$ is $(p(x))$.  We know that $g$ is surjective, because all $f(\alpha)$ map to
+some $f(x)$ so that there is an $f(x)$ for all $f(\alpha)$ such that
+$g(f(x)) = f(\alpha)$.  Thus, by Theorem 6.13, $F[x]/(p(x))$ is isomorphic
+to $F[\alpha]$.
+
+\end{enumerate}
+\end{enumerate}
 \end{document}

### 2019-12-02 hw9/MSimonsHW9.tex
hw9 typos

@@
 \usepackage{amsmath}
+\usepackage{mathtools}
+\DeclarePairedDelimiterX\setc[2]{\{}{\}}{\,#1 \;\delimsize\vert\; #2\,}
 
@@
 
-\item TODO Rewrite this and replace $(q_{1}(x))$ with $(q_{i}(x))$
-
+\item
 First, assume $(p(x))$ is maximal.  Let
 $p(x) = q_{1}(x)q_{2}(x) ... q_{n}(x)$ be the prime factorization of $p(x)$.
-Therefore $(p(x)) \subset (q_{1}(x))$ since $q_{1}(x)$ divides $p(x)$.
-Since $(p(x))$ is maximal, either $(p(x)) = (q_{1}(x))$ or $F[x] = (q_{1}(x))$.
+Because $q_{i}(x)$ divides $p(x)$ for some nonconstant $q_{i}(x)$ ($1 \leq i \leq n$),
+ $(p(x)) \subset (q_{i}(x))$.
+Since $(p(x))$ is maximal, either $(p(x)) = (q_{i}(x))$ or $F[x] = (q_{i}(x))$.
 \\ \\
-Assume $(p(x)) = (q_{1}(x))$.  Therefore $p(x)$ must be some divisor of
-$q_{1}(x)$ such that $q_{1}(x) = p(x)q_{2}^{-1}(x) ... q_{n}^{-1}(x)$.  This
-implies that $q_{2}(x), q_{3}(x), ..., q_{n}(x)$ are units, which are nonzero
-constants.  If $p(x)$ is the product of an irreducible polynomial $q_{1}(x)$
+If $F[x] = (q_{i}(x))$, then $q_{i}(x)$ must
+be a unit, which is a contradiction.  Thus, $(p(x)) = (q_{i}(x))$.
+Therefore $p(x)$ must be some divisor of
+$q_{i}(x)$ such that
+\[
+q_{i}(x) = p(x)q_{1}^{-1}(x)q_{2}^{-1}(x) ... q_{i-1}^{-1}(x)q_{i+1}^{-1}(x) ... q_{n}^{-1}(x).
+\]
+\\
+This
+implies that $q_{1}(x)$, $q_{2}(x)$, ... $q_{i-1}(x)$, $q_{i+1}(x)$ ... $q_{n}^(x)$
+are units, which are nonzero constants.  If $p(x)$ is the product of an
+irreducible polynomial $q_{i}(x)$
 and several nonzero constant polynomials, then $p(x)$ is irreducible.
-\\ \\
-Now assume $F[x] = (q_{1}(x))$.  If this is the case, then $q_{1}(x)$ must
-be a unit, which is a contradiction.
 \\ \\
@@
 \item
-By the Division Algorithm, $a(x) = b(x)q(x) + r(x)$ such that
-$0 \leq deg r(x) < deg b(x)$.  By Theorem 6.1, $b(x)q(x) \in I$ and
+By the Division Algorithm,
+\[
+a(x) = b(x)q(x) + r(x)
+\] \[
+0 \leq \deg{r(x)} < \deg{b(x)}.
+\]
+\\
+By Theorem 6.1, $b(x)q(x) \in I$ and
 $a(x) - b(x)q(x) = r(x) \in I$.
@@
 \item Let $a(x)$ by any nonzero polynomial in $I$.  By the Division Algorithm,
-$a(x) = p(x)q(x) + r(x)$ such that $0 \leq deg r(x) < deg p(x)$.  However,
-$p(x)$ is of minimal degree, so $deg r(x) = 0$.  Therefore, $p(x)$ divides
+$a(x) = p(x)q(x) + r(x)$ such that $0 \leq \deg{r(x)} < \deg{p(x)}$.  However,
+$p(x)$ is of minimal degree, so $\deg{r(x)} = 0$.  Therefore, $p(x)$ divides
 all $a(x) \in I$.
@@
 \item
-Let $I = \{f(x) \in F[x] | f(\alpha) = 0\}$.  We know that $I$ is an ideal of
+Let $I = \setc*{ f(x) \in F[x]}{f(\alpha) = 0 }$.  We know that $I$ is an ideal of
 $F[x]$ because for all $f_{1}(x)$, $f_{2}(x) \in I$,
@@
 \]
-So $f_{1}(x) - f_{2}(x) \in I$.  For all $g(x) \in F[x]$ and $f(x) \in I$,
+So $f_{1}(x) - f_{2}(x) \in I$.  And, for all $g(x) \in F[x]$ and $f(x) \in I$,
 \[
@@
 
-\item Let $I = \{f(x) \in \mathbb{Q} | f(\sqrt[7]{2}) = 0\}$.
+\item Let $I = \setc*{f(x) \in \mathbb{Q}}{f(\sqrt[7]{2}) = 0}$.
 Let $p(x) = x^2 - 2$.  By Eisenstein's Criterion, $x^7 - 2$ is irreducible, and
 $p(\sqrt[7]{2}) = 0$ so $p(x) \in I$.  By problem $4a$, any nonzero
-$g(x) \in I$ must be divisible by $p(x)$, meaning that $deg$ $g \geq 7$.
+$g(x) \in I$ must be divisible by $p(x)$, meaning that $\deg{g} \geq 7$.
 

### 2019-12-05 hw8/MSimonsHW8.tex
reworking hw8 problem 5
Fixing problems 4 and 5
Typo in number 3
typo in 2a

--- 2019-11-05 hw8/MSimonsHW8.tex
@@
 \item
-Let $f(x) = x^3 + 2x + 1$.  We know that $f(x)$ is irreducible in
-$\mathbb{Z}/3\mathbb{Z}$ because $f(0) = f(1) = f(2) = 1$.  Therefore,
+Let $f(x) = x^3 + 2x + 1$.  We know that $f(x)$ is irreducible over
+$\mathbb{Z}/3\mathbb{Z}$ because $f(0) = f(1) = f(2) = 1$ and $\deg f(x) = 3$.
+Therefore,
 $K$ is a field.
-
-\item TODO
 
@@
 $rd$ be any element of $(d)$.
-Therefore, $rd = r(au + bv) = rau + rbv = a(ru) + b(rv) \subseteq (a,b)$.
+Therefore, $rd = r(au + bv) = rau + rbv = a(ru) + b(rv) \in (a,b)$.
 Thus $(d) \subseteq (a,b)$. \\ \\
@@
 
+\item
+Let $f(x) \in I$ and $g(x) \in \mathbb{Z}[x]$ such that
+\[
+f(x) = a_{0} + a_{1}x + a_{2}x^{2} + ... + a_{n-1}x^{n-1} + 2a_{n}x^n
+\]
+and
+\[
+g(x) = b_{0} + b_{1}x + b_{2}x^{2} + ... + b_{m-1}x^{m-1} + 2b_{m}x^m.
+\]
+Then,
+\[
+f(x)*g(x) = a_{0}b_{0} + (a_{0}b_{1} + a_{1}b_{0})x + (a_{0}b_{2}+a_{1}b{1}+a_{2}b_{0}) + ... + 2a_{n}b_{m}x^{n+m}
+\]
+and
+\[
+g(x)*f(x) = b_{0}a_{0} + (b_{0}a_{1} + b_{1}a_{0})x + (b_{0}a_{2}+b_{1}a{1}+b_{2}a_{0}) + ... + 2b_{m}a_{n}x^{m+n}.
+\]
+Since the leading coefficients of $f(x)*g(x)$ and $g(x)*f(x)$ are both even,
+$f(x)*g(x) \in I$ and $g(x)*f(x) \in I$.  Therefore, $I$ is an ideal of $\mathbb{Z}[x]$.
+
+\item Let $f(x)$, $g(x) \in I$ such that $g(x) \neq 0_{F}$.
+By the Division Algorithm, $g(x) = f(x)q(x) + r(x)$ such that $r(x) = 0_{F}$
+or $\deg r(x) < \deg g(x)$.  By the definition of $I$,
+\[
+g(7) = f(7)q(7) + r(7)
+\]
+\[
+0 = f0*q(7) + r(7)
+\]
+\[
+0 = r(7).
+\]
+Therefore, $r(x) \in I$ and $f(x)$ divides $g(x)$.  Therefore, $I$ is
+finitely-generated.
+
 \end{enumerate}

### 2019-12-05 hw8/MSimonsHW8.tex
2b
Finished fixing hw8

@@
 \item Since $(x^7 + 25x^6 - 25x + 5)$ is a nonconstant polynomial in
-$\mathbb{Q}$, $\mathbb{Q}/(x^7 + 25x^6 - 25x + 5)$ is a field if and only if
-$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$.  We know that
-$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$ by Eisenstein's
-Criterion for prime $5$.  Thus, $\mathbb{Q}/(x^7 + 25x^6 - 25x + 5)$ is a field.
+$\mathbb{Q}$[x], $\mathbb{Q}[x]/(x^7 + 25x^6 - 25x + 5)$ is a field if and only if
+$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$[x].  We know that
+$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$[x] by Eisenstein's
+criterion for prime $5$.  Thus, $\mathbb{Q}[x]/(x^7 + 25x^6 - 25x + 5)$ is a field.
 
@@
 irreducible in $\mathbb{Z}/2\mathbb{Z}$ because
-$\overline{f}(0) = \overline{f}(1) = 1$.  Since $\overline{f}(x)$ is
+$\overline{f}(0) = \overline{f}(1) = 1$ and $\deg \overline{f}(x) = 3$.  Since $\overline{f}(x)$ is
 irreducible in $\mathbb{Z}/2\mathbb{Z}$, $f(x)$ is irreducible in $\mathbb{Q}$,
@@
 \item Only first-degree and second-degree polynomials can be irreducible in
-$\mathbb{R}[x]$.  Since $(x^5 + 42x^4 + \pi x^3 -1729x^2 + ln(2)x - 2019)$
+$\mathbb{R}[x]$.  Since $(x^5 + 42x^4 + \pi x^3 -1729x^2 + \ln (2)x - 2019)$
 is a fifth-degree polynomial, it is reducible in $\mathbb{R}[x]$.  Therefore
@@
 $K$ is a field.
+\item
+We know that $f(t)$ does not have any roots in $K$ because $a \in \mathbb{Z}/3\mathbb{Z}$
+is a root of $f(t)$ if and only if $t-a$ is a factor of $f(t)$.  By definition of
+$\mathbb{Z}/3\mathbb{Z}$, $a$ can only be 0, 1, or 2.  However, by the Division
+Algorithm,
+\[
+t^3 + 2t + 1 = t(t^2 + 2) + 1,
+\]
+\[
+t^3 + 2t + 1 = (t+1)(t^2 - t) + 1,
+\]
+and
+\[
+t^3 + 2t + 1 = (t+2)(t^2 - 2t) + 1.
+\]
+Therefore, $f(t)$ has no roots.
 
